### 2015-12-02 paper/typeinst.tex
Part about CPM

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{url}
\urldef{\mailsa}\path|alexa.schlegel@gmail.com|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\renewcommand*\familydefault{\sfdefault}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Temporal Development of Overlapping Communities in Co-Authorship Networks}

% a short form should be given in case it is too long for the running head
\titlerunning{Temporal Development of Overlapping Communities}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Alexa Schlegel%
}
%
\authorrunning{Temporal Development of Overlapping Communities}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Freie Universit{\"a}t Berlin, Institute of Computer Science\\
\mailsa\\
}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Temporal Development of Overlapping Communities in Co-Authorship Networks}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words.
\keywords{co-authorship networks, scientific collaboration, overlapping community detection, temporal analysis, clique percolation}
\end{abstract}

\section{Introduction}
introduction to the topic\\
why i am doing this\\
motivation\\
research question\\
limitations with my dataset\\
goal of the paper\\

\section{Related Work}
what areas belong to related work, what is covered here
other papers doing the same as I want to do
community detection and temporal aspects of network analysis

\subsection{Sientific collaboration}
TODO, why is this important

\subsection{Co-Authorship Network}
short summary networks, social networks, SNA, co-authorship networks, references to who studied those networks

\subsection{Communities in Social Networks}
Definition of communities\\
\cite{girvan2002community}\\
\url{http://www.ams.org/notices/200909/rtx090901082p.pdf}\\
\cite{palla2005uncovering}\\
\cite{fortunato2010community}\\
\url{https://en.wikipedia.org/wiki/Community_structure}

\subsubsection{Community Detection Algorithms in General}
[TODO short summary with further readings]
maybe short classification of algorithms from~\cite{fortunato2010community}\\
divisive and agglomerative methos\\

\subsubsection{Detecting Overlapping Communities}
Need for detecting overlapping communities in co-authorship networks [TODO - find citation]

[However, in real graphs vertices are often shared between communities (Section 2), and the issue of detecting overlapping communities has become quite popular in the last few years. We devote this section to the main techniques to detect overlapping communities.~\cite{fortunato2010community}]

One poplular method for detecting overlapping communities is the \emph{clique percolation method} introduced by Palla et. al in 2005~\cite{palla2005uncovering}

Other methods are summarized by Fortunato~\cite{fortunato2010community} starting page 131 [TODO summary with references]

\section{Clique Percolation Method}
Clique percolation method (CPM) is used to identify overlapping communities in networks. The following section summarizes the main findings regarding co-authorship networks and the algorithm used in the paper \emph{Uncovering the overlapping community structure of complex networks in nature and society} by Palla, Derenyi, Farkas and Vicsek.

The commmunity definition used in the paper relies on the fact that a community consists of fully connected subgraphs (\emph{cliques}), that share many nodes. \emph{$k$-cliques} are fully connected subgraphs with $k$ nodes. A community in this context is called a \emph{$k$-clique-community}, which is defined as a union of all $k$-cliques, which can be reached from each other through a number of \emph{adjacent $k$-cliques}. Two $k$-cliques are called adjacent if they share $k-1$ nodes. An example can be seen in figure [TODO image $k$-clique and $k$-clique-community].

\subsection{Algorithm}
Based on the explained community definition the algorithm consists of the following steps, which will be explained in more detail. [TODO an example of a graph in each step of the algorithm can be seen in figure X].

\begin{enumerate}
\item Find all \emph{maximal cliques}, these are cliques that are not part of larger cliques.
\item Prepare clique-clique overlap matrix.
\item Treshold the matrix.
\item All connected components represent a community.
\end{enumerate}

\subsubsection{Find all maximal cliques}
Maximal cliques cannot be subsets of larger cliques, that is why they are detected in decreasing order of their size. The largest possible clique size $s_max$ is determinde by the maximal degree $d_max$ found in the network.

\begin{enumerate}
\item[(1)] Determine $s=s_{max}$.
\item[(2)] Repeatedly choose a node $v$ from the graph and
\item[(3)] extract all cliques of size $s$ containing $v$ then
\item[(4)] delete the node and its edges.
\item[(5)] When no nodes are left set $s=s-1$ and start with (2) on the original graph.
\end{enumerate}

The set of already found cliques do influence the found cliques in later steps, as the later found cliques are smaller. The detailed algorithm for step (3) finding cliques of size $s$ of $v$ can be looked up in supplemtary material to the paper on section 1.1.2, page 3. The result of this a set of all maximal cliques, this set contains $n_c$ cliques.

\subsubsection{Prepare clique-clique overlap matrix}
The dimension of the overlap matrix is $n_c \times n_c$. Each row and column represent a clique, the matrix element (not the diagonal entries) are the common nodes those cliques share. The diagonal entries represent the size of the cliques.

\subsubsection{Treshold the matrix}
All off-diagonal entry smaller than $k-1$ and diagonal entries smaller than $k$ are set to $0$, remaining elements are set to $1$, resulting in a binary matrix, representing a network of cliques.

\subsubsection{All connected components represent a community}
Looking at the binary matrix (or resulting graph) we just need to look for connected components, those represent the $k$-clique-communities.

\subsection{Details on $k$ \& $w^*$ for co-authorship networks}
calculation of link weights $1/(n-1)$, with $n$ number of authors per paper. Treshold $w^*$ for link weights. This is how collaboration is weighted or defined.

\subsection{Summary of variables an measured statistics}
Maybe important what should I measure in my network.

[TODO what $k$ to choose]

\subsection{Main Findings of the paper}
Overlaps in networks are significant. The distributions introduced in the paper (community size, community degree, overlap size, membership number) reveal universal features of networks. The network of communities has non-trivial correlations and specific scaling properties. Providing a tool with which to enterprete the inner organisation of large networks.

\section{Community Evolution based in CPM}
TODO

\section{Limitations and Implications regarding my dataset}
what are problems with this method and what are implications regarding my dataset and network

{
	\bibliographystyle{plain}
	\bibliography{../papers}
}

\end{document}

### 2015-12-02 paper/typeinst.tex
some text to evolution

@@
 \section{Clique Percolation Method}
+\label{cpm}
 Clique percolation method (CPM) is used to identify overlapping communities in networks.
@@
 
+\subsection{Construction of the co-authorship network}
+TODO, how are weights calculated in this network, what is a collaboration here.
+
 \subsection{Algorithm}
@@
 [TODO an example of a graph in each step of the algorithm can be seen in figure X].
+The starting point for the algorithm is a undirected unweighted graph.
+In section \ref{cpm-construction} we talk about generating an unweighted collaboration, co-authorship graph.
 
@@
 
-\subsection{Details on $k$ \& $w^*$ for co-authorship networks}
-calculation of link weights $1/(n-1)$, with $n$ number of authors per paper. Treshold $w^*$ for link weights. This is how collaboration is weighted or defined.
+\subsection{Construction of the network and Details on $k$ \& $w^*$ for co-authorship networks}
+\label{cpm-construction}
+also talk about choosing the right k and the rigth trashhold.
+Calculation of link weights $1/(n-1)$, with $n$ number of authors per paper.
+Treshold $w^*$ for link weights.
+This is how collaboration is weighted or defined.
 
@@
 \section{Community Evolution based in CPM}
-TODO
+\label{evolution}
+Palla et.~al developed \cite{palla2007quantifying} in 2007 an algorithm based on clique percolation that allows us to investigate the time dependance of overlapping communities on a large scale, thus uncovering basic relationships characterizing community evolution.
+sumary
+
+\subsection{Construction of the time dependant networks}
+Event in the network are paper publications.
+Social connection between people start before event and lastet for some time after the event, the higher the fequency the closer the relationship[TODO citeSocial intertia in collaboration networks, Ramosco and Morris 2006]
+
+Weight is $n/(n-1)$ for each paper and its collaborators.
+The \emph{link weight} between to nodes $a$ and $b$ at a certain time $t$ is calculated as
+
+$$w_{a,b}(t)= \sum_{i}^{} w_i e^{\frac{-\lambda \left|t-t_i\right|}{w_i}}$$
+
+The summation runs over all collaboration event in which $a$ and $b$ are involved.
+The event $i$ occurs at time $t_i$ and the corresponding edge weight at this time is called $w_i$.
+This function which looks like a decay functions kind of models the strenght of collaboration between authors over time considering all event ever occured in time.
+
+A treshhold $w^*$ is used to only include certain edges to the time dependant graph. So for each timestep a graph can be constructed based on the collaboration strenght in each time step.
+
+here in the co-authorship network $k=3, w^*=1.0$ is used.
+
+what are the time steps for co-author network [TODO find out read again]
+
+\subsection{Algorithm}
+The algorithm uses the clique percolation method to find communities in each time depandent graph.
+The starting point is set of an undirected and unweighted  graphs for each timestep (snapshots usually called in other papers)
+
+\begin{enumerate}
+\item[(1)] Extract communities with CPM for each time step.
+\item[(2)] Match the set of communities at succeeding time steps (far from trivial). 
+\end{enumerate}
+
+As (1) was already explained in section~\ref{cpm} we focus on (2) the matching of set of communities between consecutive time steps [is it really consecutive or only after one another?]
+
+\subsection{Summary of variables an measured statistics}
+the overall coverage of the community structure (ratio of nodes contained in at least one community) is measured\\
+distribution of community size is measured too\\
+
+\subsection{Main Findings of the paper}
+difference between big and small communities and development over time
 

### 2015-12-02 paper/typeinst.tex
stichpunkte

@@
 \section{Introduction}
-introduction to the topic\\
-why i am doing this\\
-motivation\\
-research question\\
-limitations with my dataset\\
-goal of the paper\\
+introduction to the topic, scientific collaboration, co-authorship networks, social networks\\
+motivation: dataset, already constructed co-authorship network, based on very simple modeling of collaboration, self constructed trashhold\\
+research question: how do communities within co-authorship networks evolve over time?
+in geochemistry people often focus on one isotope system, and stick to this topic.
+do researchers in geochemistry really focus on one topic or do they change the field over time?
+why do they change field and were do they change to?
+by analysing the network over time this question could be answered maybe\\
+goal of the paper of the paper is to find an appropriate method for analysing scientific collaboration networks over time\\
 
 \section{Related Work}
-what areas belong to related work, what is covered here
-other papers doing the same as I want to do
-community detection and temporal aspects of network analysis
+community detection in complex and large graphs\\
+different methods of community detection algorithms\\
+communities in collaboration networks (co-authorship)\\
+temporal aspects of communities\\
+time slicing and dividing the network into snapshots\\
+algorithms and implementations\\
+focus not on different time slicing methods but more on community detection\\
+references to temporal stuff [TODO cite moody]
 
 \subsection{Sientific collaboration}
-TODO, why is this important
+TODO definition [TODO cite]\\
+based on who borad or narrow the definition of collaboration is, a function/measurement for edgeweight can be chosen
 
 \subsection{Co-Authorship Network}
-short summary networks, social networks, SNA, co-authorship networks, references to who studied those networks
+short summary networks, social networks, SNA, co-authorship networks\\
+references to who studied those networks [Newmann and Barabasi] just references\\
+nodes are authors, links are collaboration, wights for nodes and edges\\
 
 \subsection{Communities in Social Networks}
-Definition of communities\\
+Definition of communities, there is no proper definition yet\\
 \cite{girvan2002community}\\
@@
 \url{https://en.wikipedia.org/wiki/Community_structure}
+most real world networks contain parts in which nodes are more highly conected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modeuls [TODO cite], they have no wiedely accepted unique definition.
+the detection algorithms mainly define what a community is.
 
@@
 maybe short classification of algorithms from~\cite{fortunato2010community}\\
+maybe there are so many aproaches\\
 divisive and agglomerative methos\\
@@
 \subsection{Construction of the co-authorship network}
-TODO, how are weights calculated in this network, what is a collaboration here.
+TODO, how are weights calculated in this network, what is a collaboration here. $n/(n-1)$ with $n$ auhors for one publication
 
@@
 The starting point for the algorithm is a undirected unweighted graph.
-In section \ref{cpm-construction} we talk about generating an unweighted collaboration, co-authorship graph.
+In section \ref{cpm-construction} we talk about generating an unweighted collaboration, co-authorship graph using a treshhold.
 
@@
 \label{cpm-construction}
-also talk about choosing the right k and the rigth trashhold.
+talk about choosing the right $k$ and the rigth trashhold $w^*$.
 Calculation of link weights $1/(n-1)$, with $n$ number of authors per paper.
@@
 This is how collaboration is weighted or defined.
+all links smaller than $w^*$ are removed.\\
+how to chose the right $k$, usually between $3$ and $6$, then $w^*$ is ajusted\\
 
@@
 Maybe important what should I measure in my network.
-
-[TODO what $k$ to choose]
+those measurement describe the quality of those detected communities\\
+summary of variable\\
 
@@
 The network of communities has non-trivial correlations and specific scaling properties.
-Providing a tool with which to enterprete the inner organisation of large networks.
+Providing a tool with which to enterprete the inner organisation of large networks.[TODO cite]
 
@@
 Palla et.~al developed \cite{palla2007quantifying} in 2007 an algorithm based on clique percolation that allows us to investigate the time dependance of overlapping communities on a large scale, thus uncovering basic relationships characterizing community evolution.
-sumary
 
@@
 Event in the network are paper publications.
-Social connection between people start before event and lastet for some time after the event, the higher the fequency the closer the relationship[TODO citeSocial intertia in collaboration networks, Ramosco and Morris 2006]
+Social connection between people start before event and last for some time after the event, the higher the fequency the closer the relationship[TODO citeSocial intertia in collaboration networks, Ramosco and Morris 2006]
 
@@
 The algorithm uses the clique percolation method to find communities in each time depandent graph.
-The starting point is set of an undirected and unweighted  graphs for each timestep (snapshots usually called in other papers)
+The starting point is set of an undirected and unweighted  graphs for each timestep (snapshots usually called in other papers).
 
@@
 
-As (1) was already explained in section~\ref{cpm} we focus on (2) the matching of set of communities between consecutive time steps [is it really consecutive or only after one another?]
+As (1) was already explained in section~\ref{cpm} we focus on (2) the matching of set of communities between consecutive time steps [is it really consecutive or only after one another?]\\
+
+As overlapping communities are included, this step is not trivial. The relative node overlap $C(A,B)$ between two nodes $A$ and $B$ in a simple way can be defined as
+
+$$C(A,B) = \frac{ \left| A \cap B\right| }{\left| A \cup B\right|}$$
+
+[TODO this method is not working for overlapping communities, paper is desribing an over complicated matching algorithm :(]
 
@@
 \subsection{Main Findings of the paper}
-difference between big and small communities and development over time
+difference between big and small communities and development over time\\
+small communities live longer if members stay the same\\
+if members change, they die\\
+big communities live longer if members are changed permanently\\
+if members stay the same they die\\
 
-\section{Limitations and Implications regarding my dataset}
-what are problems with this method and what are implications regarding my dataset and network
+\section{Implications regarding my dataset}
+what are problems with this method and what are implications regarding my dataset and network\\
+I need a new function for calculating edge weights\\
+find out what time slices are possible in my data[TODO]\\
+try out CPM (there is an implementation in R) with static network\\
+calculate measurement to see if quality of communities is good, find out right $k$ and $w^*$, maybe use the one from paper but, evaluate if those are good\\
+create snapshots of the paper and try if provided function for calculating weight at timesteps can be used\\
+find an implementation of the community mapping for each time step\\
+
+\section{Future Work}
+find out what other methods are out there with implementations, I dont have the time to implement a cutting edge algorithm\\
+compare my network/community structure to null-model(or other) or to other social network to see if everything is nice\\
+maybe some time should be invested for finding a good representation for edge weights calculation, related to collaboration definition\\
+next time choose a less complicated topic\\
 

### 2015-12-04 paper/typeinst.tex
part 4 finished for today, still figures needed

@@
 
-\section{Community Evolution based in CPM}
+\section{Community Evolution based on CPM}
 \label{evolution}
-Palla et.~al developed \cite{palla2007quantifying} in 2007 an algorithm based on clique percolation that allows us to investigate the time dependance of overlapping communities on a large scale, thus uncovering basic relationships characterizing community evolution.
+Palla et.~al~\cite{palla2007quantifying} developed an algorithm based on clique percolation (see section~\ref{cpm}) that allows the investigation of overlapping communities over time.
+They uncovered basic relationships characterizing community evolution within a co-authorship network and a phone-call network.
+The following section describes the main steps of the algorithm.
+A short summary of their main findings can be found in section~\ref{evolution-findings}.
 
-\subsection{Construction of the time dependant networks}
-Event in the network are paper publications.
-Social connection between people start before event and last for some time after the event, the higher the fequency the closer the relationship[TODO citeSocial intertia in collaboration networks, Ramosco and Morris 2006]
+\subsection{Algorithm}
+\label{evolution-algo}
+The starting point of the algorithm is a set of undirected and unweighted  graphs for each timestep.
+How to produce those temporal graphs is explained later in section~\ref{evolution-constr}.
+In general the algorithm uses the clique percolation method to find communities in each temporal graph, and matches the communities of consecutive timesteps.
 
-Weight is $n/(n-1)$ for each paper and its collaborators.
-The \emph{link weight} between to nodes $a$ and $b$ at a certain time $t$ is calculated as
+\begin{enumerate}
+\small
+\item[(1)] Extract communities with CPM for each graph $g_t$ at time step $t$.
+\item[(2)] Match set of communities at consecutive time steps of graph $g_t$, $g_{t+1}$, as follows:
+	\begin{enumerate}
+		\item[(2.1)] Construct joint graph $g_{\cup}=g_t \cup g_{t+1}$.
+		\item[(2.2)] Extract communities $V$ with CPM in joint graph $g_{\cup}$.
+		\item[(2.3)] For each extracted community $V_i$: 
+		\begin{itemize}
+			\item Extract communities in $g_t$ and $g_{t+1}$ that are contained in $V_i$.
+			\item Calculate relative overlap for each pair.
+			\item Match communities in decending order.
+		\end{itemize}
+	\end{enumerate}
+\item[(3)] Gap filling.
+\end{enumerate}
+
+The following describe the steps (2) and (3) in detail.
+Step (1) was explained in section~\ref{cpm} already.
+
+\subsubsection{Matching Communities}
+\label{evolution-algo-matching}
+For matching communities, the \emph{relative node overlap} $C(A,B)$ between two nodes $A$ and $B$, in a simple way, is defined as follows:
+$$C(A,B) = \frac{ \left| A \cap B\right| }{\left| A \cup B\right|}$$
+As overlapping communities are allowed the matching from consecutive time steps in descending order of their relative node overlap can lead to missmatching.
+For example when small communities gain a lot of members or vice versa. An example for this problem is given in figure~X [TODO-PIC].
+As a solution, for each time steps $t$ and $t+1$ a joint graph $g_{\cup}$ is constructed, containing all links from both networks.
+Let $D$ be the set of communities at time step $t$ and $E$ the set of communities at time step $t+1$.
+The set of communities from the joint graph $g_{\cup}$ are extracted using CPM again and are called $V$.
+For any community $D_i \in D$ or $E_j \in E$ exactly one community $V_k \in V$ can be found.
+For checking weather $E_i$ or $D_j$ is contained in $V_k$ the links are compared instead of nodes.
+For each community $V_i \in V$ the set of communities $D_i^k \in D$ and $E_j^k \in E$ contained in $V_i$ are extracted.
+Now the relative node overlap between every possible pair can be calculated as follows
+$$C^k_{i,j} = \frac{\left| D_i^k \cap E_j^k\right|}{\left| D_i^k\cup E_j^k \right| }$$
+and the pairs can be matched in descending order.
+
+In figures~X three examples are given: figXa is a simple matching of a propagating community, figXb showing two merging communities with one community dying and figXc showning the splitting of a community into two communities with one community is new born.
+
+\subsubsection{Gap Filling}
+In some cases a community which was disintegrated at a certain time step suddenly reappear in a later timestep, due to low publishing rates for example.
+That means a newborn community includes a formerly dead community.
+This problem is overcome by just fillig the gap with the last step of the almost disintegrated community.
+
+\subsection{Construction of the temporal co-authorship network}
+\label{evolution-constr}
+Events in the co-authorship are paper publications.
+The social connection between people writing a paper together usually starts before the event and last for some time after the event.
+The higher the fequency the closer the relationship~\cite{ramasco2006social}.
+
+The edge weight resulting from one paper is $n/(n-1)$ with $n$ authors. The \emph{link weight} between to nodes $a$ and $b$ at a certain time $t$ is calculated as
 
@@
 The event $i$ occurs at time $t_i$ and the corresponding edge weight at this time is called $w_i$.
-This function which looks like a decay functions kind of models the strenght of collaboration between authors over time considering all event ever occured in time.
+This function which is a decay functions kind of models the strenght of collaboration between authors over time considering all event ever occured in time.
 
-A treshhold $w^*$ is used to only include certain edges to the time dependant graph. So for each timestep a graph can be constructed based on the collaboration strenght in each time step.
+A treshhold $w^*$ is used to only include certain edges to the emporal graph. So for each timestep a graph can be constructed based on the collaboration strenght per time step.
 
-here in the co-authorship network $k=3, w^*=1.0$ is used.
+The authors of the paper used $w^*=1.0$ for the co-authorship network, they said nothing about $\lambda$ at all. (maybe explain how $w/k$ was chosen?)
 
-what are the time steps for co-author network [TODO find out read again]
-
-\subsection{Algorithm}
-The algorithm uses the clique percolation method to find communities in each time depandent graph.
-The starting point is set of an undirected and unweighted  graphs for each timestep (snapshots usually called in other papers).
-
-\begin{enumerate}
-\item[(1)] Extract communities with CPM for each time step.
-\item[(2)] Match the set of communities at succeeding time steps (far from trivial). 
-\end{enumerate}
-
-As (1) was already explained in section~\ref{cpm} we focus on (2) the matching of set of communities between consecutive time steps [is it really consecutive or only after one another?]\\
-
-As overlapping communities are included, this step is not trivial. The relative node overlap $C(A,B)$ between two nodes $A$ and $B$ in a simple way can be defined as
-
-$$C(A,B) = \frac{ \left| A \cap B\right| }{\left| A \cup B\right|}$$
-
-[TODO this method is not working for overlapping communities, paper is desribing an over complicated matching algorithm :(]
+The dataset containes 142 month of publications, but I could find in the paper how the data was aggregated, because in the figues it looks like 50 timesteps in total.
 
 \subsection{Summary of variables an measured statistics}
-the overall coverage of the community structure (ratio of nodes contained in at least one community) is measured\\
-distribution of community size is measured too\\
+\label{evolution-vars}
+For evaluating the quality the overall coverage of the community structure (ratio of nodes contained in at least one community) is measured. Also the distribution of community size is measured.
 
 \subsection{Main Findings of the paper}
-difference between big and small communities and development over time\\
-small communities live longer if members stay the same\\
-if members change, they die\\
-big communities live longer if members are changed permanently\\
-if members stay the same they die\\
+\label{evolution-findings}
+The paper summarized differences between large and small communities and their development over time.
+Small communities live longer if the members stay the same over time.
+If members in small communities change frequently, they only live for a short time.
+Large communities live longer if members are changed permanently, if members stay the same they die quickly.
 

### 2015-12-04 paper/typeinst.tex
redo part 3 and some figures added

@@
-%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is the LaTeX source for the instructions to authors using
-% the LaTeX document class 'llncs.cls' for contributions to
-% the Lecture Notes in Computer Sciences series.
-% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
-%
-% It may be used as a template for your own input - copy it
-% to a new file with a new name and use it as the basis
-% for your article.
-%
-% NB: the document class 'llncs' has its own and detailed documentation, see
-% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \documentclass[runningheads,a4paper]{llncs}
@@
 \setcounter{tocdepth}{3}
+
 \usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{caption}
 
@@
 \section{Related Work}
+\label{related}
 community detection in complex and large graphs\\
@@
 \subsection{Sientific collaboration}
+\label{related-collabo}
 TODO definition [TODO cite]\\
@@
 \subsection{Co-Authorship Network}
+\label{related-coauth}
 short summary networks, social networks, SNA, co-authorship networks\\
@@
 \subsection{Communities in Social Networks}
+\label{related-communities}
 Definition of communities, there is no proper definition yet\\
@@
 \subsubsection{Community Detection Algorithms in General}
+\label{related-communities-general}
 [TODO short summary with further readings]
@@
 \subsubsection{Detecting Overlapping Communities}
+\label{related-communities-overlapping}
 Need for detecting overlapping communities in co-authorship networks [TODO - find citation]
@@
 \label{cpm}
-Clique percolation method (CPM) is used to identify overlapping communities in networks.
-The following section summarizes the main findings regarding co-authorship networks and the algorithm used in the paper \emph{Uncovering the overlapping community structure of complex networks in nature and society} by Palla, Derenyi, Farkas and Vicsek.
+The clique percolation method (CPM) developed by Palla et.~al~\cite{palla2007quantifying} is used to identify overlapping communities in networks.
+The authors tested and evaluated their method using a co-authorship network, protein-protein interaction network, word associations network and a network constructed from variables within the source code of an open source ftp programm.
+The following section explains the algorithm and summarizes the main findings of the paper regardin co-authorship networks.
 
-The commmunity definition used in the paper relies on the fact that a community consists of fully connected subgraphs (\emph{cliques}), that share many nodes.
+The commmunity definition the algorithm implies, relies on the fact that a community consists of fully connected subgraphs, called \emph{cliques}, that share many nodes.
 \emph{$k$-cliques} are fully connected subgraphs with $k$ nodes.
-A community in this context is called a \emph{$k$-clique-community}, which is defined as a union of all $k$-cliques, which can be reached from each other through a number of \emph{adjacent $k$-cliques}.
+In figure~\ref{fig:cliques} example of ${3,4}$-cliques are given.
+A community, in this context, is called a \emph{$k$-clique-community}, which is defined as a union of all $k$-cliques, which can be reached from each other through a number of \emph{adjacent $k$-cliques}.
 Two $k$-cliques are called adjacent if they share $k-1$ nodes.
-An example can be seen in figure [TODO image $k$-clique and $k$-clique-community].
+In figure~X the so called $k$-clique template rolling is visualized for a $3$-clique.
+A $k$-clique community is best described by relocating one node in each step until all nodes of the community are discovered.
 
-\subsection{Construction of the co-authorship network}
-TODO, how are weights calculated in this network, what is a collaboration here. $n/(n-1)$ with $n$ auhors for one publication
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{3-clique}
+        \caption{3-cliquel}
+        \label{fig:3clique}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{4-clique}
+        \caption{4-clique}
+        \label{fig:4clique}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+    %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{cliqueinside}
+        \caption{4-clique inside a graph}
+        \label{fig:cliqueInside}
+    \end{subfigure}
+    \caption{Examle of cliques}\label{fig:cliques}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\textwidth]{rolling.png}
+	\caption{Template rolling for a $3$-clique}
+	\label{fig:rolling}
+\end{figure}
 
 \subsection{Algorithm}
-Based on the explained community definition the algorithm consists of the following steps, which will be explained in more detail.
-[TODO an example of a graph in each step of the algorithm can be seen in figure X].
-The starting point for the algorithm is a undirected unweighted graph.
-In section \ref{cpm-construction} we talk about generating an unweighted collaboration, co-authorship graph using a treshhold.
+The starting point for the algorithm is a undirected and unweighted graph. In section \ref{cpm-construction} we talk about generating the  unweighted co-authorship.
+Based on the explained community definition the algorithm consists of the following steps:
+
+[TODO: weiter ueberarbeiten ab hier]\\
 
@@
 Looking at the binary matrix (or resulting graph) we just need to look for connected components, those represent the $k$-clique-communities.
+
+\subsection{Construction of the co-authorship network}
+TODO, how are weights calculated in this network, what is a collaboration here. $n/(n-1)$ with $n$ auhors for one publication
 
@@
 
+say how big is my data\\
+what about time complexity\\
+
 \section{Future Work}
@@
 next time choose a less complicated topic\\
+how to visualize the development?
 
-{
 \bibliographystyle{plain}
 \bibliography{../papers}
-}
 

### 2015-12-04 paper/typeinst.tex
part 3 and some figures

@@
 \label{cpm}
-The clique percolation method (CPM) developed by Palla et.~al~\cite{palla2007quantifying} is used to identify overlapping communities in networks.
+The clique percolation method (CPM) developed by Palla et.~al~\cite{palla2007quantifying} is used to identify overlapping communities in unweighted and undirected networks.
 The authors tested and evaluated their method using a co-authorship network, protein-protein interaction network, word associations network and a network constructed from variables within the source code of an open source ftp programm.
@@
 \emph{$k$-cliques} are fully connected subgraphs with $k$ nodes.
-In figure~\ref{fig:cliques} example of ${3,4}$-cliques are given.
+In figure~\ref{fig:cliques} example of $\{3,4\}$-cliques are given.
 A community, in this context, is called a \emph{$k$-clique-community}, which is defined as a union of all $k$-cliques, which can be reached from each other through a number of \emph{adjacent $k$-cliques}.
 Two $k$-cliques are called adjacent if they share $k-1$ nodes.
-In figure~X the so called $k$-clique template rolling is visualized for a $3$-clique.
-A $k$-clique community is best described by relocating one node in each step until all nodes of the community are discovered.
+In figure~\ref{fig:rolling} the so called $k$-clique template rolling is visualized for a $3$-clique.
+A $k$-clique-community is best described by relocating one node until all nodes of the community are discovered.
 
@@
 \subsection{Algorithm}
-The starting point for the algorithm is a undirected and unweighted graph. In section \ref{cpm-construction} we talk about generating the  unweighted co-authorship.
+\label{cpm-algo}
+The starting point for the algorithm is a undirected and unweighted graph. In section \ref{cpm-construction} we talk about generating the  unweighted co-authorship graph.
 Based on the explained community definition the algorithm consists of the following steps:
 
-[TODO: weiter ueberarbeiten ab hier]\\
+\begin{enumerate}
+\small
+\item[(1)] Find all \emph{maximal cliques}.
+\item[(2)] Prepare clique-clique overlap matrix (clique graph).
+\item[(3)] Treshold the matrix with a certain $k$.
+\item[(4)] Each connected component in the clique graph form a $k$-clique-community.
+\end{enumerate}
+
+\subsubsection{(1) Find all maximal cliques}
+Instead of finding all $k$-cliques (it is a polynomial problem) as a first step.
+The algorithm searches for all maximal cliques, this can be done in exponential time the authors state.
+Maximal cliques cannot be subsets of larger cliques.
+That is why they are detected in decreasing order of their size.
+The largest possible clique size $s_{max}$ is determinde by the maximal degree $d_{max}$ found in the network.
 
 \begin{enumerate}
-\item Find all \emph{maximal cliques}, these are cliques that are not part of larger cliques.
-\item Prepare clique-clique overlap matrix.
-\item Treshold the matrix.
-\item All connected components represent a community.
+\small
+\item[(1)] Determine $s=s_{max}$.
+\item[(2)] Repeatedly choose a node $v$ from the graph:
+	\begin{enumerate}
+		\item[(2.1)] Extract all cliques of size $s$ containing $v$.
+		\item[(2.2)] Delete the node and its edges.
 	\end{enumerate}
-
-\subsubsection{Find all maximal cliques}
-Maximal cliques cannot be subsets of larger cliques, that is why they are detected in decreasing order of their size.
-The largest possible clique size $s_max$ is determinde by the maximal degree $d_max$ found in the network.
-
-\begin{enumerate}
-\item[(1)] Determine $s=s_{max}$.
-\item[(2)] Repeatedly choose a node $v$ from the graph and
-\item[(3)] extract all cliques of size $s$ containing $v$ then
-\item[(4)] delete the node and its edges.
-\item[(5)] When no nodes are left set $s=s-1$ and start with (2) on the original graph.
+\item[(3)] When no nodes are left set $s=s-1$ and start with (2) on the original graph.
 \end{enumerate}
@@
 The set of already found cliques do influence the found cliques in later steps, as the later found cliques are smaller.
-The detailed algorithm for step (3) finding cliques of size $s$ of $v$ can be looked up in supplemtary material to the paper on section 1.1.2, page 3.
-The result of this a set of all maximal cliques, this set contains $n_c$ cliques.
+The detailed algorithm for step (2.1) finding cliques of size $s$ of $v$ can be looked up in supplemtary material to the paper on section 1.1.2, page 3.
+The result of this step is a set of all maximal cliques, an example can be seen in figure~\ref{fig:3clique}.
+This set contains $n_c$ cliques.
 
-\subsubsection{Prepare clique-clique overlap matrix}
-The dimension of the overlap matrix is $n_c \times n_c$.
-Each row and column represent a clique, the matrix element (not the diagonal entries) are the common nodes those cliques share.
-The diagonal entries represent the size of the cliques.
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.8\textwidth]{allmaxcliques.png}
+		\caption{All maximal cliques in a graph. Each color represents a maximal clique.}
+		\label{fig:allmaxcliques}
+\end{center}
+\end{figure}
 
-\subsubsection{Treshold the matrix}
-All off-diagonal entry smaller than $k-1$ and diagonal entries smaller than $k$ are set to $0$, remaining elements are set to $1$, resulting in a binary matrix, representing a network of cliques.
+\subsubsection{(2) Prepare clique-clique overlap matrix (clique graph)}
+The dimension of the overlap matrix is $n_c \times n_c$. Each row and column represent a clique.
+All non-diagonal matrix elements represent the number of nodes those cliques share.
+The diagonal entries represent the size of the corresponding clique.
+This matrix is only generated once.
+In figure~\ref{fig:matrix} the clique-clique overlap matrix of graph in figure~\ref{fig:allmaxcliques} and the coressponding clique graph is shown.
 
-\subsubsection{All connected components represent a community}
-Looking at the binary matrix (or resulting graph) we just need to look for connected components, those represent the $k$-clique-communities.
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.8\textwidth]{matrix.png}
+		\caption{The clique-clique overlap matrix and the coresponding clique graph.
+The number inside the node is the number of nodes belonging to that community, the width of the edge represents the shared nodes.}
+		\label{fig:matrix}
+\end{center}		
+\end{figure}
 
-\subsection{Construction of the co-authorship network}
-TODO, how are weights calculated in this network, what is a collaboration here. $n/(n-1)$ with $n$ auhors for one publication
+\subsubsection{(3) Treshold the matrix}
+All off-diagonal entries smaller than $k-1$ and diagonal entries smaller than $k$ are set to $0$.
+The remaining elements are set to $1$, resulting in a binary matrix, representing a network of cliques. The tresholding can be done repeatedly without calculating a new matrix.
 
-\subsection{Construction of the network and Details on $k$ \& $w^*$ for co-authorship networks}
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.8\textwidth]{matrixtrashed}
+		\caption{This is the resulting clique graph after the treshholding with $k=4$. All connected components do represent a $k$-clique-community. There are only two communities.}
+		\label{fig:matrix}
+\end{center}
+\end{figure}
+
+\subsubsection{(4) All connected components represent a community}
+In the resulting graph we just need to look for connected components, those represent the $k$-clique-communities.
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.8\textwidth]{result}
+		\caption{Here the two resulting $k$-clique-communities are shown.}
+		\label{fig:result}
+\end{center}
+\end{figure}
+
+\subsection{Construction of the co-authorship and choosing the right $k$ and trashold.}
 \label{cpm-construction}
-talk about choosing the right $k$ and the rigth trashhold $w^*$.
-Calculation of link weights $1/(n-1)$, with $n$ number of authors per paper.
-Treshold $w^*$ for link weights.
-This is how collaboration is weighted or defined.
-all links smaller than $w^*$ are removed.\\
-how to chose the right $k$, usually between $3$ and $6$, then $w^*$ is ajusted\\
+The edge weights are calculated with $n/(n-1)$ with $n$ as number of auther per publication.
+This results in modeling the collaboration between fewer authors as more intensive that looking at a higher number of authors.  
+To generate an unweighted network all edges need to be removed under a certain treshold $w^*$, all others are replaced by weight $1$.
+Increasing $w^*$ results in fewer edges throughout the network, but stronger links and fewer detected communities.
 
-\subsection{Summary of variables an measured statistics}
-Maybe important what should I measure in my network.
-those measurement describe the quality of those detected communities\\
-summary of variable\\
+In addition a good $k$ needs to be chosen. As $k$ is increased the detected $k$-clique-communities shrink, but at the same time become more cohesive (stronger connected).
+
+So a good balance between $k$ and $w^*$ needs to be found resulting in a community structure which is highly structured.
+
+The authors state that $k$ is usually betweem between $3$ and $6$.
+If the number of links in a network are increased above some point a giant component evolves and covers the underlying community structure.
+So for each $k$ the treshold $w^*$ is lowered until the larges component becomes twice as big as the second largest component.
+For really choosing the best $k$ some further characteristics describing the community structure need to be investigated, see Supplementary Information of~\cite{palla2005uncovering} for more details.
+
+\subsection{Summary of measured statistics}
+A node $i$ of a network has the following characteristics:
+
+\begin{description}
+	\item[membership number \textbf{$m_i$}] \dots number of communities the node belongs to
+	\item[overlap size $s^\texttt{ov}_{\alpha,\beta}$] \dots between two communities $\alpha$ and $\beta$
+	\item[community degree $d_{\alpha}^\texttt{com}$] \dots number of links a community $\alpha$ has
+	\item[community size $s_{\alpha}^\texttt{com}$] \dots number of nodes belonging to community $\alpha$
+\end{description}
+
+The distributions of all characteristics are measured and analysed.
 
@@
 The distributions introduced in the paper (community size, community degree, overlap size, membership number) reveal universal features of networks.
-The network of communities has non-trivial correlations and specific scaling properties.
-Providing a tool with which to enterprete the inner organisation of large networks.[TODO cite]
+The network of communities has non-trivial correlations and specific scaling properties.~\cite{palla2005uncovering}
 

### 2015-12-05 paper/typeinst.tex
some introduction

@@
 \usepackage{caption}
+\usepackage{url}
 
-\usepackage{url}
 \urldef{\mailsa}\path|alexa.schlegel@gmail.com|
@@
 
-\section{Introduction}
-introduction to the topic, scientific collaboration, co-authorship networks, social networks\\
-motivation: dataset, already constructed co-authorship network, based on very simple modeling of collaboration, self constructed trashhold\\
-research question: how do communities within co-authorship networks evolve over time?
-in geochemistry people often focus on one isotope system, and stick to this topic.
-do researchers in geochemistry really focus on one topic or do they change the field over time?
-why do they change field and were do they change to?
-by analysing the network over time this question could be answered maybe\\
-goal of the paper of the paper is to find an appropriate method for analysing scientific collaboration networks over time\\
+\section{Introduction and Motivation}
+A social network is a representation of a social structure consisting of actors (e.g. individuals, affiliations) and their social interactions.
+The network model conceptualizes (e.g. social, economic, political) structure as lasting pattern of interactions between actors.~\cite{wasserman1994social}
+
+A co-authorship networks is a (scientific) collaboration network, where actors are scientists and the social interaction is the collaboration work resulting in publishing a paper together.
+Networks are in mathematical terms graphs, so they consist of nodes (vertex) and links (edges).
+In a co-authorship graph nodes are individual authors who are considered connected if the have co-aothored a paper.~\cite{newman2001structure}
+
+Usually those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different measurement, detection and evolution of communities and many more.~\cite{barabasi2002evolution, newman2001structure, newman2004coauthorship}
+
+This seminar paper is motivated by a dataset consisting of 2277 publications related to geochemistry about stable metal isotopes (calcium, magnesium, lithium, siliium, etc.).
+This data was used to build an cummulated co-authorship network with an very simple approach to model collaboration:
+The dataset was collected using the bibliographic database scopus.
+It is an almost complete dataset starting from 1997/98 until 2014.
+The dataset consists of authors and co-athors, title, year, abstract and affiliations.
+Basic netowrk analysis had already been conducted for example centrality measurement, community detection, degree distribution and average degree.
+
+As the dataset includes temporal information, the question arises how do communities within this type of co-authorship network evlolve over time.
+In geochemistry people often tend to focus on one isotope system, and stick to this topic for a long time.
+Do researchers in geochemistry really focus on one topic or do they change the field over time?
+
+The goal of this seminar paper therefeore is to find and explain an already established and well understood/studied method for analysing the temporal development of communities within co-authorship networks.
+The main point is to understand the undelying algorithm in detail and to find out implications and challenges when applying this method to the geochemistry dataset.
 
@@
 All off-diagonal entries smaller than $k-1$ and diagonal entries smaller than $k$ are set to $0$.
-The remaining elements are set to $1$, resulting in a binary matrix, representing a network of cliques. The tresholding can be done repeatedly without calculating a new matrix.
+The remaining elements are set to $1$, resulting in a binary matrix, representing a network of cliques.
+The tresholding can be done repeatedly without calculating a new matrix.
+See figure~\ref{fig:matrixtrashed}.
 
@@
 		\caption{This is the resulting clique graph after the treshholding with $k=4$. All connected components do represent a $k$-clique-community. There are only two communities.}
-		\label{fig:matrix}
+		\label{fig:matrixtrashed}
 \end{center}
@@
 \subsubsection{(4) All connected components represent a community}
-In the resulting graph we just need to look for connected components, those represent the $k$-clique-communities.
+In the resulting graph we just need to look for connected components, those represent the $k$-clique-communities. See figure~\ref{fig:result}.
 
@@
 
+{
 	\bibliographystyle{plain}
-\bibliography{../papers}
+	\bibliography{papers}
+}
 

### 2015-12-05 paper/typeinst.tex
some related work and stucture

@@
 \label{related}
-community detection in complex and large graphs\\
-different methods of community detection algorithms\\
-communities in collaboration networks (co-authorship)\\
-temporal aspects of communities\\
-time slicing and dividing the network into snapshots\\
-algorithms and implementations\\
-focus not on different time slicing methods but more on community detection\\
-references to temporal stuff [TODO cite moody]
+I am foucsing on community detection algorithms in general and especially for co-aothorship networks.
+A second topic is how to track communities over time and how to model scientific collaboration in relation to edge weights.
 
-\subsection{Sientific collaboration}
-\label{related-collabo}
-TODO definition [TODO cite]\\
-based on who borad or narrow the definition of collaboration is, a function/measurement for edgeweight can be chosen
+``Most real world networks contain parts in which nodes are more highly conected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no wiedely accepted, unique definition.''~\cite{palla2005uncovering}
 
-\subsection{Co-Authorship Network}
-\label{related-coauth}
-short summary networks, social networks, SNA, co-authorship networks\\
-references to who studied those networks [Newmann and Barabasi] just references\\
-nodes are authors, links are collaboration, wights for nodes and edges\\
+The way ``more highly connected'' is preciesely defined makes the difference between community detection algorithms.
+It depends on the heuristic which is employed to identify communiteis.~\cite{porter2009communities}
 
-\subsection{Communities in Social Networks}
-\label{related-communities}
-Definition of communities, there is no proper definition yet\\
-\cite{girvan2002community}\\
-\url{http://www.ams.org/notices/200909/rtx090901082p.pdf}\\
-\cite{palla2005uncovering}\\
-\cite{fortunato2010community}\\
-\url{https://en.wikipedia.org/wiki/Community_structure}
-most real world networks contain parts in which nodes are more highly conected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modeuls [TODO cite], they have no wiedely accepted unique definition.
-the detection algorithms mainly define what a community is.
+Fortunato~\cite{fortunato2010community} gives an extended overview about different algorithms regarding community detection, to explain any would exceed the scope of this work.
+For example traditional methods include algorithms based on graph partitioning, hicharchical clustering and spectral clustering.
+there are also divisive and agglomeative algorithms, the best known one from this category is Girvan and Newman~\cite{girvan2002community}.
 
-\subsubsection{Community Detection Algorithms in General}
-\label{related-communities-general}
-[TODO short summary with further readings]
-maybe short classification of algorithms from~\cite{fortunato2010community}\\
-maybe there are so many aproaches\\
-divisive and agglomerative methos\\
+Most algorihtms determine distinctive sets of communities, but most real world networks  consists of overlapping and nested communities (e.g freidnship network of a person)~\cite{palla2005uncovering}.
 
-\subsubsection{Detecting Overlapping Communities}
-\label{related-communities-overlapping}
-Need for detecting overlapping communities in co-authorship networks [TODO - find citation]
+Fortunato~\cite{fortunato2010community} gives also an overview about algorithms how detect overlapping communities, the best known and wideliy cited is clique percolation method by Palla et.
+al~\cite{palla2005uncovering}.
+There is an implementation called cfinder\footnote{cFinder webseite todo}, and also an implementation in R igraph library\footnote{R igraph library todo link}.
 
-[However, in real graphs vertices are often shared between communities (Section 2), and the issue of detecting overlapping communities has become quite popular in the last few years.
-We devote this section to the main techniques to detect overlapping communities.~\cite{fortunato2010community}]
+community detection algorithms in co-aothorship networks\\
 
-One poplular method for detecting overlapping communities is the \emph{clique percolation method} introduced by Palla et. al in 2005~\cite{palla2005uncovering}
+development of communities over time\\
 
-Other methods are summarized by Fortunato~\cite{fortunato2010community} starting page 131 [TODO summary with references]
+temporal graphs\\
+
+how to calucalte edge weight temporal function\\
 
@@
 
-\section{Implications regarding my dataset}
+\section{Implications regarding the geochenstry dataset}
 what are problems with this method and what are implications regarding my dataset and network\\

### 2015-12-05 paper/typeinst.tex
some more related work and stichpunkte zu implication and future work

@@
 ``Most real world networks contain parts in which nodes are more highly conected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no wiedely accepted, unique definition.''~\cite{palla2005uncovering}
-
 The way ``more highly connected'' is preciesely defined makes the difference between community detection algorithms.
@@
 
-Fortunato~\cite{fortunato2010community} gives an extended overview about different algorithms regarding community detection, to explain any would exceed the scope of this work.
+Fortunato~\cite{fortunato2010community} gives an extended overview about different algorithms regarding community detection.
+To explain any would exceed the scope of this work.
 For example traditional methods include algorithms based on graph partitioning, hicharchical clustering and spectral clustering.
-there are also divisive and agglomeative algorithms, the best known one from this category is Girvan and Newman~\cite{girvan2002community}.
+There are also divisive and agglomerative algorithms.
+The best known one from this category is Girvan and Newman~\cite{girvan2002community}.
 
-Most algorihtms determine distinctive sets of communities, but most real world networks  consists of overlapping and nested communities (e.g freidnship network of a person)~\cite{palla2005uncovering}.
+Most algorihtms determine distinctive sets of communities (a node can only belong to a single community), but most real world networks  consists of overlapping and nested communities (e.g friendship network of a person)~\cite{palla2005uncovering}.
+Fortunato~\cite{fortunato2010community} gives also an overview about algorithms detecting overlapping communities.
+The best known and widely cited is \emph{clique percolation method} by Palla et. al~\cite{palla2005uncovering}.
+There is an implementation provided by the authors called CFinder\footnote{CFinder is a tool which implements the clique percolation method by Palla and finding and visualizes overlapping dense groups of nodes in networks.
+\url{http://www.cfinder.org/}, 05.12.2015, 22:43}, and also an implementation in the R igraph library\footnote{\url{http://igraph.wikidot.com/community-detection-in-r#toc0}, 05.12.2015, 22:45}.
 
-Fortunato~\cite{fortunato2010community} gives also an overview about algorithms how detect overlapping communities, the best known and wideliy cited is clique percolation method by Palla et.
-al~\cite{palla2005uncovering}.
-There is an implementation called cfinder\footnote{cFinder webseite todo}, and also an implementation in R igraph library\footnote{R igraph library todo link}.
+Not only overlapping communities exists in networks, but also communities are structured in an hirarchical way.
+Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015, Cui201485, Shen20091706}.
 
-community detection algorithms in co-aothorship networks\\
+``The main phenomena occurring in the lifetime of a community are: birth, growth, contraction, merger with other communities, split, death.''~\cite{fortunato2010community} (see figure~\ref{fig:evolution})
+The detection of dynamic communities has been studied by Palla et.~al~\cite{palla2007quantifying} using CPM for each snapshot of the graph.
+Further information on dynamic communities can be found in section 13 of~\cite{fortunato2010community}.
 
-development of communities over time\\
+\begin{figure}
+	\includegraphics[width=\textwidth]{villsize.jpg}
+	\caption{lifetime of a community}
+	\label{fig:evolution}
+\end{figure}
 
-temporal graphs\\
-
-how to calucalte edge weight temporal function\\
+As CPM is widely used method for detecting overlapping communities I will go with this method.
+The following describes the CPM and also the temporal algorithm mainly based on those tow papers~\cite{palla2005uncovering} and \cite{palla2007quantifying}.
 
@@
 
-\section{Implications regarding the geochenstry dataset}
-what are problems with this method and what are implications regarding my dataset and network\\
-I need a new function for calculating edge weights\\
-find out what time slices are possible in my data[TODO]\\
-try out CPM (there is an implementation in R) with static network\\
-calculate measurement to see if quality of communities is good, find out right $k$ and $w^*$, maybe use the one from paper but, evaluate if those are good\\
-create snapshots of the paper and try if provided function for calculating weight at timesteps can be used\\
-find an implementation of the community mapping for each time step\\
-
-say how big is my data\\
-what about time complexity\\
+\section{Implications regarding the geochemistry dataset}
+slice the network per year, 18 snapshots\\
+basic statistics about timeslices (how many publications, nodes)\\
+function for calculating edge weights\\
+apply edge weight to snapshots\\
+try out CPM (there is an implementation in R or cfinder) with static network\\
+do cpm per snapshot\\
+find out $k$\\
+adjust $w^*$\\
+calculate measurement to see if quality of communities is good (connectins inside community VS outside community), also coverage of community structure and distribution if community size (see~\ref{evolution-vars}).\\
+find an implementation or implemet community mapping\\
+time complexity whould be no problem because my dataset is not very big.\\
 
 \section{Future Work}
-find out what other methods are out there with implementations, I dont have the time to implement a cutting edge algorithm\\
-compare my network/community structure to null-model(or other) or to other social network to see if everything is nice\\
+find out what other methods are out there in more detail\\
+only had time for one method\\
+look at more recent work\\
+compare results to results in paper, similar?\\
 maybe some time should be invested for finding a good representation for edge weights calculation, related to collaboration definition\\
-next time choose a less complicated topic\\
-how to visualize the development?
+how to visualize the development\\
 

### 2015-12-05 paper/typeinst.tex
future work

@@
 \begin{abstract}
-The abstract should summarize the contents of the paper and should
-contain at least 70 and at most 150 words.
-\keywords{co-authorship networks, scientific collaboration, overlapping community detection, temporal analysis, clique percolation}
+TODO TODO TODO
+\keywords{co-authorship networks, scientific collaboration networks, overlapping community detection, temporal analysis, clique percolation, dynamic communities}
 \end{abstract}
@@
 \section{Implications regarding the geochemistry dataset}
-slice the network per year, 18 snapshots\\
-basic statistics about timeslices (how many publications, nodes)\\
-function for calculating edge weights\\
-apply edge weight to snapshots\\
-try out CPM (there is an implementation in R or cfinder) with static network\\
-do cpm per snapshot\\
-find out $k$\\
-adjust $w^*$\\
-calculate measurement to see if quality of communities is good (connectins inside community VS outside community), also coverage of community structure and distribution if community size (see~\ref{evolution-vars}).\\
-find an implementation or implemet community mapping\\
-time complexity whould be no problem because my dataset is not very big.\\
+This part describe the steps I would need to undertake to carry out a temporal analysis of communities within the geochemistry dataset or with any other dataset, which forms a collaboration network.
+
+\begin{enumerate}
+	\item[(1)] Genrate slices of the network for each year.
+	\item[(2)] Find function for calculating edge weights.
+	\item[(3)] Apply edge weights to each snapshot.
+	\item[(4)] Find out $k$.
+	\item[(5)] Adjust treshold $w^*$ according to $k$.	
+	\item[(6)] Do CPM for each snapshot.
+	\item[(7)] Conduct community mapping.
+\end{enumerate}
+
+It is also important to look at basic statistics after (1) timeslicing.
+For example to look at how many publications per timeslice, degree distributions, nodes on average per timeslice to check of timeslincing was done right or needs to be adjusted.
+The function for calculating edge weights (2) could be used from the paper (see section~\ref{evolution-constr}), but it would need to be checked if the resulting networks (3) are still valid.
+For findng the right $k$ (4) and $w^*$ (5) and extended analysis of network caracteristics like coverage of community structure and distribution if community size (see~\ref{evolution-vars}) would need to be carried out.
+Also the quality of the detected communities would need evaluation, comparing density within the community to outside the community.
+Using CFinder or R for CMP (6) detection.
+It is open to me if there is an implementation for the community mapping (7), if not I would neet to implement it.
+Time complexity will be no problem because my dataset is not very big. About 2.000 paper resulting in about 500 nodes.
 
 \section{Future Work}
-find out what other methods are out there in more detail\\
-only had time for one method\\
-look at more recent work\\
-compare results to results in paper, similar?\\
-maybe some time should be invested for finding a good representation for edge weights calculation, related to collaboration definition\\
-how to visualize the development\\
+As this paper dicusses only one method an extensive literature research should follow, finding out more methods for that problem.
+Also a closer look on recent work would be good.
+The results from this dataset should be compared to the results of Palla.
+Maybe some time should be invested for finding a good representation for edge weights calculation, related to collaboration definition.
+The visuaization of the community evolution remains open and would be a broad topic, but exciting to investigate further.
 

### 2015-12-05 paper/paper.tex
references

--- 2015-12-05 paper/typeinst.tex
@@
 
-Usually those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different measurement, detection and evolution of communities and many more.~\cite{barabasi2002evolution, newman2001structure, newman2004coauthorship}
+Usually those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different measurement, detection and evolution of communities and many more.~\cite{barabasi2002evolution}, \cite{newman2001structure} and \cite{newman2004coauthorship}.
 
@@
 Not only overlapping communities exists in networks, but also communities are structured in an hirarchical way.
-Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015, Cui201485, Shen20091706}.
+Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015}, \cite{Cui201485}, \cite{Shen20091706}.
 
@@
 \begin{enumerate}
+\small
 	\item[(1)] Genrate slices of the network for each year.

### 2015-12-06 paper/paper.tex
typo

@@
 
-``Most real world networks contain parts in which nodes are more highly conected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no wiedely accepted, unique definition.''~\cite{palla2005uncovering}
+``Most real world networks contain parts in which nodes are more highly connected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no wiedely accepted, unique definition.''~\cite{palla2005uncovering}
 The way ``more highly connected'' is preciesely defined makes the difference between community detection algorithms.

### 2015-12-06 paper/paper.tex
typo

--- 2015-12-05 paper/paper.tex
@@
 
-``Most real world networks contain parts in which nodes are more highly conected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no wiedely accepted, unique definition.''~\cite{palla2005uncovering}
+``Most real world networks contain parts in which nodes are more highly connected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no widely accepted, unique definition.''~\cite{palla2005uncovering}
 The way ``more highly connected'' is preciesely defined makes the difference between community detection algorithms.

### 2016-01-02 paper/paper.tex
abstract and correction of itriduction and motivation

@@
 \begin{abstract}
-TODO TODO TODO
+Detection of overlapping communities plays an important role when it comes to analysing scientific collaboration using social networks.
+This paper focuses on describing a method to analyze the temporal development of overlapping communities within co-authorship networks.
+The paper mainly relies on the work of Palla~et~al.
+using the clique percolation method for community extraction.
+The main goal was to find and understand an appropriate algorithm, which can be applied to an existing dataset of scientific publications.
+Implications regarding further actions and time complexity are discussed.
+
 \keywords{co-authorship networks, scientific collaboration networks, overlapping community detection, temporal analysis, clique percolation, dynamic communities}
@@
 \section{Introduction and Motivation}
-A social network is a representation of a social structure consisting of actors (e.g. individuals, affiliations) and their social interactions.
-The network model conceptualizes (e.g. social, economic, political) structure as lasting pattern of interactions between actors.~\cite{wasserman1994social}
+A \emph{social network} is a representation of a social structure consisting of actors, e.g.~individuals, affiliations, and their social interactions.
+The network model conceptualizes e.g.~social, economic or political structures as lasting pattern of interactions between actors.~\cite{wasserman1994social}
 
-A co-authorship networks is a (scientific) collaboration network, where actors are scientists and the social interaction is the collaboration work resulting in publishing a paper together.
-Networks are in mathematical terms graphs, so they consist of nodes (vertex) and links (edges).
-In a co-authorship graph nodes are individual authors who are considered connected if the have co-aothored a paper.~\cite{newman2001structure}
+A \emph{co-authorship networks} is a scientific collaboration network, where actors are scientists and the social interaction is collaboration work resulting in publishing papers together.
+In mathematical terms networks are graphs, therefore they consist of nodes (vertex) and links (edges).
+In a co-authorship network nodes are individual authors who are considered connected if they co-aothored a paper.~\cite{newman2001structure}
 
-Usually those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different measurement, detection and evolution of communities and many more.~\cite{barabasi2002evolution}, \cite{newman2001structure} and \cite{newman2004coauthorship}.
+Usually those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different network measurements, detection and evolution of communities and many more.
+See~\cite{barabasi2002evolution}, \cite{newman2001structure} and \cite{newman2004coauthorship} for more details.
 
-This seminar paper is motivated by a dataset consisting of 2277 publications related to geochemistry about stable metal isotopes (calcium, magnesium, lithium, siliium, etc.).
-This data was used to build an cummulated co-authorship network with an very simple approach to model collaboration:
-The dataset was collected using the bibliographic database scopus.
-It is an almost complete dataset starting from 1997/98 until 2014.
-The dataset consists of authors and co-athors, title, year, abstract and affiliations.
-Basic netowrk analysis had already been conducted for example centrality measurement, community detection, degree distribution and average degree.
+This seminar paper is motivated by a dataset consisting of $2.277$ publications related to geochemistry focusing on papers talking about stable metal isotopes (e.g.~potassium, magnesium, lithium, silicon).
+This data was used to build an cummulated co-authorship network using an very simple approach to model collaboration.
 
-As the dataset includes temporal information, the question arises how do communities within this type of co-authorship network evlolve over time.
+The dataset was collected using the bibliographic database scopus\footnote{\url{http://www.scopus.com/}} and includes publications starting from 1997/98 until 2014.
+The dataset consists of authors, co-athors, title, year, abstract and affiliations.
+A basic network analysis had already been conducted for example centrality measurement, community detection, degree distribution and average degree.
+
+As the data set includes temporal information~(publishing year), the following question arises: How do communities within this type of co-authorship network evlolve over time?
 In geochemistry people often tend to focus on one isotope system, and stick to this topic for a long time.
-Do researchers in geochemistry really focus on one topic or do they change the field over time?
+Do researchers in geochemistry really focus on one specific topic or do they change the field over time?
 
-The goal of this seminar paper therefeore is to find and explain an already established and well understood/studied method for analysing the temporal development of communities within co-authorship networks.
+The goal of this seminar paper therefeore is to find and explain an already established and well understood method for analysing the temporal development of communities within co-authorship networks.
 The main point is to understand the undelying algorithm in detail and to find out implications and challenges when applying this method to the geochemistry dataset.

### 2016-01-02 paper/paper.tex
correct related work

@@
 \label{related}
-I am foucsing on community detection algorithms in general and especially for co-aothorship networks.
-A second topic is how to track communities over time and how to model scientific collaboration in relation to edge weights.
-
+The related work focuses on algorithms for community detection especially for co-aothorship networks and how to track those detected communities over time.
 ``Most real world networks contain parts in which nodes are more highly connected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no widely accepted, unique definition.''~\cite{palla2005uncovering}
@@
 
-Fortunato~\cite{fortunato2010community} gives an extended overview about different algorithms regarding community detection.
+Fortunato~\cite{fortunato2010community} gives an extended overview about various types of community detection algorithms.
 To explain any would exceed the scope of this work.
@@
 
-Most algorihtms determine distinctive sets of communities (a node can only belong to a single community), but most real world networks  consists of overlapping and nested communities (e.g friendship network of a person)~\cite{palla2005uncovering}.
+Most algorihtms determine distinctive sets of communities, so a node can only belong to a single community.
+Most real world networks  consists of overlapping and nested communitiesm e.g.~friendship network of a person~\cite{palla2005uncovering}.
 Fortunato~\cite{fortunato2010community} gives also an overview about algorithms detecting overlapping communities.
-The best known and widely cited is \emph{clique percolation method} by Palla et. al~\cite{palla2005uncovering}.
-There is an implementation provided by the authors called CFinder\footnote{CFinder is a tool which implements the clique percolation method by Palla and finding and visualizes overlapping dense groups of nodes in networks.
-\url{http://www.cfinder.org/}, 05.12.2015, 22:43}, and also an implementation in the R igraph library\footnote{\url{http://igraph.wikidot.com/community-detection-in-r#toc0}, 05.12.2015, 22:45}.
+The best known and widely cited is the \emph{clique percolation method (CPM)} by Palla et~al.~\cite{palla2005uncovering}.
+There is an implementation provided by the authors, called \emph{CFinder}\footnote{CFinder is a tool which implements the clique percolation method by Palla and finding and visualizing overlapping dense groups of nodes in networks.
+\url{http://www.cfinder.org/}, 05.12.2015, 22:43}, and an implementation in the R igraph library\footnote{\url{http://igraph.wikidot.com/community-detection-in-r#toc0}, 05.12.2015, 22:45}.
 
@@
 
-``The main phenomena occurring in the lifetime of a community are: birth, growth, contraction, merger with other communities, split, death.''~\cite{fortunato2010community} (see figure~\ref{fig:evolution})
-The detection of dynamic communities has been studied by Palla et.~al~\cite{palla2007quantifying} using CPM for each snapshot of the graph.
+Looking at the temporal development of communities ``the main phenomena occurring in the lifetime of a community are: birth, growth, contraction, merger with other communities, split, death''~\cite{fortunato2010community} (see figure~\ref{fig:evolution}).
+The detection of dynamic communities has been studied by Palla et~al.~\cite{palla2007quantifying} using CPM for each snapshot of the graph.
 Further information on dynamic communities can be found in section 13 of~\cite{fortunato2010community}.
@@
 
-As CPM is widely used method for detecting overlapping communities I will go with this method.
-The following describes the CPM and also the temporal algorithm mainly based on those tow papers~\cite{palla2005uncovering} and \cite{palla2007quantifying}.
+As CPM is a widely used method for detecting overlapping communities I will explain this method in more detail.
+The following sections describe the CPM and also the temporal algorithm mainly based on the two papers of Palla et~al.~\cite{palla2005uncovering} and~\cite{palla2007quantifying}.
 

### 2016-01-02 paper/paper.tex
CPM section

@@
 \toctitle{Temporal Development of Overlapping Communities in Co-Authorship Networks}
-\tocauthor{Authors' Instructions}
 \maketitle
@@
 Not only overlapping communities exists in networks, but also communities are structured in an hirarchical way.
-Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015}, \cite{Cui201485}, \cite{Shen20091706}.
+Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015}, \cite{Cui201485} and~ \cite{Shen20091706}.
 
@@
 \label{cpm}
-The clique percolation method (CPM) developed by Palla et.~al~\cite{palla2007quantifying} is used to identify overlapping communities in unweighted and undirected networks.
+The clique percolation method (CPM) developed by Palla et~al.~\cite{palla2007quantifying} is used to identify overlapping communities in unweighted and undirected networks.
 The authors tested and evaluated their method using a co-authorship network, protein-protein interaction network, word associations network and a network constructed from variables within the source code of an open source ftp programm.
-The following section explains the algorithm and summarizes the main findings of the paper regardin co-authorship networks.
+The following section explains the algorithm and summarizes the main findings of the paper regarding co-authorship networks.
 
-The commmunity definition the algorithm implies, relies on the fact that a community consists of fully connected subgraphs, called \emph{cliques}, that share many nodes.
+The underlying commmunity definition relies on the fact that a community consists of fully connected subgraphs, called \emph{cliques}.
 \emph{$k$-cliques} are fully connected subgraphs with $k$ nodes.
-In figure~\ref{fig:cliques} example of $\{3,4\}$-cliques are given.
+In figure~\ref{fig:cliques} an example of $\{3,4\}$-cliques are given.
 A community, in this context, is called a \emph{$k$-clique-community}, which is defined as a union of all $k$-cliques, which can be reached from each other through a number of \emph{adjacent $k$-cliques}.
@@
 \label{cpm-algo}
-The starting point for the algorithm is a undirected and unweighted graph. In section \ref{cpm-construction} we talk about generating the  unweighted co-authorship graph.
+The starting point for the algorithm is an undirected and unweighted graph. In section \ref{cpm-construction} we talk about generating the  unweighted co-authorship graph.
 Based on the explained community definition the algorithm consists of the following steps:
@@
 \small
-\item[(1)] Find all \emph{maximal cliques}.
-\item[(2)] Prepare clique-clique overlap matrix (clique graph).
-\item[(3)] Treshold the matrix with a certain $k$.
+\item[(1)] Find all maximal cliques.
+\item[(2)] Prepare clique-clique overlap matrix, or clique graph.
+\item[(3)] Threshold the matrix with a certain $k$.
 \item[(4)] Each connected component in the clique graph form a $k$-clique-community.
@@
 \subsubsection{(1) Find all maximal cliques}
-Instead of finding all $k$-cliques (it is a polynomial problem) as a first step.
-The algorithm searches for all maximal cliques, this can be done in exponential time the authors state.
+Instead of finding all $k$-cliques, as a first step, the algorithm searches for all maximal cliques.
+Instead of finding all $k$-cliques, which is a polynomial problem, his can be done in exponential time the authors state.
 Maximal cliques cannot be subsets of larger cliques.
@@
 The detailed algorithm for step (2.1) finding cliques of size $s$ of $v$ can be looked up in supplemtary material to the paper on section 1.1.2, page 3.
-The result of this step is a set of all maximal cliques, an example can be seen in figure~\ref{fig:3clique}.
-This set contains $n_c$ cliques.
+The result of this step is a set with size $n_c$ of all maximal cliques, an example can be seen in figure~\ref{fig:3clique}.
 
@@
 
-\subsubsection{(2) Prepare clique-clique overlap matrix (clique graph)}
+\subsubsection{(2) Prepare clique-clique overlap matrix, or clique graph}
 The dimension of the overlap matrix is $n_c \times n_c$. Each row and column represent a clique.
@@
 This matrix is only generated once.
-In figure~\ref{fig:matrix} the clique-clique overlap matrix of graph in figure~\ref{fig:allmaxcliques} and the coressponding clique graph is shown.
+In figure~\ref{fig:matrix} the clique-clique overlap matrix of the graph of figure~\ref{fig:allmaxcliques} and the coressponding clique graph is shown.
 
@@
 
-\subsubsection{(3) Treshold the matrix}
+\subsubsection{(3) Threshold the matrix}
 All off-diagonal entries smaller than $k-1$ and diagonal entries smaller than $k$ are set to $0$.
 The remaining elements are set to $1$, resulting in a binary matrix, representing a network of cliques.
-The tresholding can be done repeatedly without calculating a new matrix.
-See figure~\ref{fig:matrixtrashed}.
+The thresholding can be done repeatedly without calculating a new matrix, see figure~\ref{fig:matrixtrashed}.
 
@@
 	\includegraphics[width=0.8\textwidth]{matrixtrashed}
-		\caption{This is the resulting clique graph after the treshholding with $k=4$. All connected components do represent a $k$-clique-community. There are only two communities.}
+		\caption{This is the resulting clique graph after the thresholding with $k=4$. All connected components do represent a $k$-clique-community. In this example are two communities.}
 		\label{fig:matrixtrashed}
@@
 
-\subsubsection{(4) All connected components represent a community}
-In the resulting graph we just need to look for connected components, those represent the $k$-clique-communities. See figure~\ref{fig:result}.
+\subsubsection{(4) Each connected component in the clique graph form a $k$-clique-community.}
+In the resulting graph we need to look for connected components, those represent the $k$-clique-communities, see figure~\ref{fig:result}.
 
@@
 
-\subsection{Construction of the co-authorship and choosing the right $k$ and trashold.}
+\subsection{Construction of the co-authorship network, choosing $k$ and threshold $w^*$.}
 \label{cpm-construction}
-The edge weights are calculated with $n/(n-1)$ with $n$ as number of auther per publication.
-This results in modeling the collaboration between fewer authors as more intensive that looking at a higher number of authors.  
-To generate an unweighted network all edges need to be removed under a certain treshold $w^*$, all others are replaced by weight $1$.
+The edge weights are calculated with $$\frac{n}{n-1}$$ with $n$ beeing the number of authers per publication.
+This results in modeling the collaboration between fewer authors as more intensive than the collaboration between a higher number of authors.  
+To generate an unweighted network all edges with an edgeweight below a certain threshold $w^*$ need to be removed, all others edgweights are replaced by weight $1$.
 Increasing $w^*$ results in fewer edges throughout the network, but stronger links and fewer detected communities.
 
-In addition a good $k$ needs to be chosen. As $k$ is increased the detected $k$-clique-communities shrink, but at the same time become more cohesive (stronger connected).
-
+In addition a good $k$ needs to be chosen. When $k$ is increased the detected $k$-clique-communities shrink, but at the same time become more cohesive (stronger connected).
 So a good balance between $k$ and $w^*$ needs to be found resulting in a community structure which is highly structured.
 
-The authors state that $k$ is usually betweem between $3$ and $6$.
+The authors state that $k$ is usually between $3$ and $6$.
 If the number of links in a network are increased above some point a giant component evolves and covers the underlying community structure.
@@
 For really choosing the best $k$ some further characteristics describing the community structure need to be investigated, see Supplementary Information of~\cite{palla2005uncovering} for more details.
-
-\subsection{Summary of measured statistics}
-A node $i$ of a network has the following characteristics:
-
-\begin{description}
-	\item[membership number \textbf{$m_i$}] \dots number of communities the node belongs to
-	\item[overlap size $s^\texttt{ov}_{\alpha,\beta}$] \dots between two communities $\alpha$ and $\beta$
-	\item[community degree $d_{\alpha}^\texttt{com}$] \dots number of links a community $\alpha$ has
-	\item[community size $s_{\alpha}^\texttt{com}$] \dots number of nodes belonging to community $\alpha$
-\end{description}
-
-The distributions of all characteristics are measured and analysed.
 

### 2016-01-02 paper/paper.tex
community evolution correction

@@
 \item[(4)] Each connected component in the clique graph form a $k$-clique-community.
+\item[(5)] Post-processing.
 \end{enumerate}
@@
 
+\subsubsection{(5) Post-processing.}
+The last setp of the algorithm assigns left over nodes, if possible, to communities.
+A node which is only connected to one certain community and is not part of a commnity already is assiciated with this community.
+The number of nodes belonging to a community can be increased.
+
 \begin{figure}
@@
 
-\subsection{Construction of the co-authorship network, choosing $k$ and threshold $w^*$.}
+\subsection{Construction of the co-authorship network}
 \label{cpm-construction}
@@
 
-\section{Community Evolution based on CPM}
+\section{Community Evolution}
 \label{evolution}
-Palla et.~al~\cite{palla2007quantifying} developed an algorithm based on clique percolation (see section~\ref{cpm}) that allows the investigation of overlapping communities over time.
+Palla et~al.~\cite{palla2007quantifying} developed an algorithm based on clique percolation (see section~\ref{cpm}) that allows the investigation of overlapping communities over time.
 They uncovered basic relationships characterizing community evolution within a co-authorship network and a phone-call network.
@@
 \label{evolution-algo}
-The starting point of the algorithm is a set of undirected and unweighted  graphs for each timestep.
-How to produce those temporal graphs is explained later in section~\ref{evolution-constr}.
-In general the algorithm uses the clique percolation method to find communities in each temporal graph, and matches the communities of consecutive timesteps.
+The starting point of the algorithm is an undirected and unweighted graph for each timestep.
+The construction of those temporal graphs is explained in section~\ref{evolution-constr}.
+In general, the algorithm uses the clique percolation method to find communities in each temporal graph, and after that matches the communities of consecutive timesteps.
 
@@
 	\end{enumerate}
-\item[(3)] Gap filling.
+\item[(3)] Post-processing.
 \end{enumerate}
 
-The following describe the steps (2) and (3) in detail.
-Step (1) was explained in section~\ref{cpm} already.
+The following describes steps (2) and (3) in detail.
+Step (1) was already explained in section~\ref{cpm}.
 
@@
 \label{evolution-algo-matching}
-For matching communities, the \emph{relative node overlap} $C(A,B)$ between two nodes $A$ and $B$, in a simple way, is defined as follows:
-$$C(A,B) = \frac{ \left| A \cap B\right| }{\left| A \cup B\right|}$$
+For matching communities, the \emph{relative node overlap} $C(A,B)$ between two nodes $A$ and $B$, in a simple way, is defined as
+$$C(A,B) = \frac{ \left| A \cap B\right| }{\left| A \cup B\right|}.$$
 As overlapping communities are allowed the matching from consecutive time steps in descending order of their relative node overlap can lead to missmatching.
@@
 As a solution, for each time steps $t$ and $t+1$ a joint graph $g_{\cup}$ is constructed, containing all links from both networks.
-Let $D$ be the set of communities at time step $t$ and $E$ the set of communities at time step $t+1$.
-The set of communities from the joint graph $g_{\cup}$ are extracted using CPM again and are called $V$.
+Let $D$ be the set of communities at time step $t$ and $E$ the set of communities at time step $t+1$. The set of communities from the joint graph $g_{\cup}$ are extracted using CPM and are called $V$.
 For any community $D_i \in D$ or $E_j \in E$ exactly one community $V_k \in V$ can be found.
@@
 For each community $V_i \in V$ the set of communities $D_i^k \in D$ and $E_j^k \in E$ contained in $V_i$ are extracted.
-Now the relative node overlap between every possible pair can be calculated as follows
+Now the relative node overlap between every possible pair can be calculated as with
 $$C^k_{i,j} = \frac{\left| D_i^k \cap E_j^k\right|}{\left| D_i^k\cup E_j^k \right| }$$
@@
 
-In figures~X three examples are given: figXa is a simple matching of a propagating community, figXb showing two merging communities with one community dying and figXc showning the splitting of a community into two communities with one community is new born.
+In figures~X three examples are given: figXa is a simple matching of a propagating community, figXb showing two merging communities with one community dying and figXc showing the splitting of a community into two communities with one community is born.
 
-\subsubsection{Gap Filling}
+\subsubsection{Post-processing}
 In some cases a community which was disintegrated at a certain time step suddenly reappear in a later timestep, due to low publishing rates for example.
 That means a newborn community includes a formerly dead community.
-This problem is overcome by just fillig the gap with the last step of the almost disintegrated community.
+This problem is overcome by just fillig the gap with the last step of the almost disintegrated community, this is calle gap-filling.
 
-\subsection{Construction of the temporal co-authorship network}
+\subsection{Construction of the temporal co-authorship networks}
 \label{evolution-constr}
-Events in the co-authorship are paper publications.
+Events in the co-authorship network are publications.
 The social connection between people writing a paper together usually starts before the event and last for some time after the event.
@@
 
-The edge weight resulting from one paper is $n/(n-1)$ with $n$ authors. The \emph{link weight} between to nodes $a$ and $b$ at a certain time $t$ is calculated as
+The edge weight resulting from one paper is $n/(n-1)$ with $n$ as thr number of authors. The edge weight between to nodes $a$ and $b$ at a certain time $t$ is calculated as
 
-$$w_{a,b}(t)= \sum_{i}^{} w_i e^{\frac{-\lambda \left|t-t_i\right|}{w_i}}$$
+$$w_{a,b}(t)= \sum_{i}^{} w_i e^{\frac{-\lambda \left|t-t_i\right|}{w_i}}.$$
 
@@
 The event $i$ occurs at time $t_i$ and the corresponding edge weight at this time is called $w_i$.
-This function which is a decay functions kind of models the strenght of collaboration between authors over time considering all event ever occured in time.
+This decay function models the strenght of collaboration between authors over time considering all events ever occured in time.
 
-A treshhold $w^*$ is used to only include certain edges to the emporal graph. So for each timestep a graph can be constructed based on the collaboration strenght per time step.
+A threshold $w^*$ is used to only include certain edges to the temporal graph. So for each timestep a graph can be constructed based on the collaboration strenght per time step.
 
-The authors of the paper used $w^*=1.0$ for the co-authorship network, they said nothing about $\lambda$ at all. (maybe explain how $w/k$ was chosen?)
+The authors of the paper used $w^*=1.0$ for the co-authorship network.
+No details about $\lambda$ is given in the paper.
 
-The dataset containes 142 month of publications, but I could find in the paper how the data was aggregated, because in the figues it looks like 50 timesteps in total.
+[TODO explain how w and ka are chosen.]
 
-\subsection{Summary of variables an measured statistics}
-\label{evolution-vars}
-For evaluating the quality the overall coverage of the community structure (ratio of nodes contained in at least one community) is measured. Also the distribution of community size is measured.
+The data set used in the paper contained 142 month of publications. Details about data aggregation are not given, but looking at the figures it looks like 50 timeslices.
 
@@
 The paper summarized differences between large and small communities and their development over time.
-Small communities live longer if the members stay the same over time.
+Small communities live longer if their members stay the same over time.
 If members in small communities change frequently, they only live for a short time.

### 2016-01-02 paper/paper.tex
last part correct

@@
 No details about $\lambda$ is given in the paper.
-
-[TODO explain how w and ka are chosen.]
-
 The data set used in the paper contained 142 month of publications. Details about data aggregation are not given, but looking at the figures it looks like 50 timeslices.
@@
 
-\section{Implications regarding the geochemistry dataset}
-This part describe the steps I would need to undertake to carry out a temporal analysis of communities within the geochemistry dataset or with any other dataset, which forms a collaboration network.
+\section{Implications and Efficiency of the Algorithm}
+This part describe the steps I would need to undertake to carry out a temporal analysis of communities within the geochemistry data set or with any other data set, which forms a collaboration network.
 
@@
 
-It is also important to look at basic statistics after (1) timeslicing.
-For example to look at how many publications per timeslice, degree distributions, nodes on average per timeslice to check of timeslincing was done right or needs to be adjusted.
-The function for calculating edge weights (2) could be used from the paper (see section~\ref{evolution-constr}), but it would need to be checked if the resulting networks (3) are still valid.
-For findng the right $k$ (4) and $w^*$ (5) and extended analysis of network caracteristics like coverage of community structure and distribution if community size (see~\ref{evolution-vars}) would need to be carried out.
+It is nessesary to evaluate the quality of the resulting network after step (1) timeslicing, by looking at the basic statistics (number of publications per per timeslice, degree distribution, nodes on average per timeslice).
+The function for calculating edge weights (2) could be taken from the paper (see section~\ref{evolution-constr}), but should be followed by checking if the resulting networks after step (3) are still valid.
+For finding the right $k$ (4) and $w^*$ (5) and extended analysis of network caracteristics like coverage of community structure and distribution if community size (see~\ref{evolution-vars}) would need to be carried out.
 Also the quality of the detected communities would need evaluation, comparing density within the community to outside the community.
-Using CFinder or R for CMP (6) detection.
-It is open to me if there is an implementation for the community mapping (7), if not I would neet to implement it.
-Time complexity will be no problem because my dataset is not very big. About 2.000 paper resulting in about 500 nodes.
+For step (1) CFinder or R could be used.
+It is open to me if there is an implementation for the community mapping (7), if not this step would need to be implemented.
+
+Determination of all cliques within a graph is a non-polynomial problem.
+The authos state that the required CPU time depends strongly on the structure of the input data, so no closed formula to estimate the system size depenance can be given.
+A complete CPM analysis for a co-authorship networl with $127.000$ links takes less than 2 hours on a PC\footnote{No details about the PC are given in the paper.}.
+I assume time complexity will not be a problem because my dataset contains $18.404$ eges in total, when not applying any threshold.
 
 \section{Future Work}
-As this paper dicusses only one method an extensive literature research should follow, finding out more methods for that problem.
-Also a closer look on recent work would be good.
-The results from this dataset should be compared to the results of Palla.
-Maybe some time should be invested for finding a good representation for edge weights calculation, related to collaboration definition.
+As this paper dicusses only one popular method, an extensive literature research should follow, finding out more methods solving the problem.
+Also a closer look at more recent work would be nesessary.
+It would be also interesting to find a good model for calculating edge weights with respect to scientific collaboration definitions.
 The visuaization of the community evolution remains open and would be a broad topic, but exciting to investigate further.

### 2016-01-02 paper/paper.tex
rechtschreibung

@@
 \begin{abstract}
-Detection of overlapping communities plays an important role when it comes to analysing scientific collaboration using social networks.
+Detection of overlapping communities plays an important role when it comes to analyzing scientific collaboration using social networks.
 This paper focuses on describing a method to analyze the temporal development of overlapping communities within co-authorship networks.
@@
 A \emph{social network} is a representation of a social structure consisting of actors, e.g.~individuals, affiliations, and their social interactions.
-The network model conceptualizes e.g.~social, economic or political structures as lasting pattern of interactions between actors.~\cite{wasserman1994social}
+The network model conceptualizes e.g.~social, economic or political structures as lasting patterns of interactions between actors.~\cite{wasserman1994social}
 
-A \emph{co-authorship networks} is a scientific collaboration network, where actors are scientists and the social interaction is collaboration work resulting in publishing papers together.
+A \emph{co-authorship network} is a scientific collaboration network, where actors are scientists and the social interaction is collaboration work resulting in publishing papers together.
 In mathematical terms networks are graphs, therefore they consist of nodes (vertex) and links (edges).
-In a co-authorship network nodes are individual authors who are considered connected if they co-aothored a paper.~\cite{newman2001structure}
+In a co-authorship network nodes are individual authors who are considered connected if they co-authored a paper.~\cite{newman2001structure}
 
-Usually those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different network measurements, detection and evolution of communities and many more.
+Usually, those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different network measurements, detection and evolution of communities and many more.
 See~\cite{barabasi2002evolution}, \cite{newman2001structure} and \cite{newman2004coauthorship} for more details.
@@
 This seminar paper is motivated by a dataset consisting of $2.277$ publications related to geochemistry focusing on papers talking about stable metal isotopes (e.g.~potassium, magnesium, lithium, silicon).
-This data was used to build an cummulated co-authorship network using an very simple approach to model collaboration.
+This data was used to build a cummulated co-authorship network using an very simple approach to model collaboration.
 
 The dataset was collected using the bibliographic database scopus\footnote{\url{http://www.scopus.com/}} and includes publications starting from 1997/98 until 2014.
-The dataset consists of authors, co-athors, title, year, abstract and affiliations.
+The dataset consists of authors, co-authors, title, year, abstract and affiliations.
 A basic network analysis had already been conducted for example centrality measurement, community detection, degree distribution and average degree.
 
-As the data set includes temporal information~(publishing year), the following question arises: How do communities within this type of co-authorship network evlolve over time?
+As the data set includes temporal information~(publishing year), the following question arises: How do communities within this type of co-authorship network evolve over time?
 In geochemistry people often tend to focus on one isotope system, and stick to this topic for a long time.
@@
 
-The goal of this seminar paper therefeore is to find and explain an already established and well understood method for analysing the temporal development of communities within co-authorship networks.
-The main point is to understand the undelying algorithm in detail and to find out implications and challenges when applying this method to the geochemistry dataset.
+The goal of this seminar paper therefor is to find and explain an already established and well-understood method for analyzing the temporal development of communities within co-authorship networks.
+The main point is to understand the underlying algorithm in detail and to find out implications and challenges when applying this method to the geochemistry dataset.
 
@@
 \label{related}
-The related work focuses on algorithms for community detection especially for co-aothorship networks and how to track those detected communities over time.
+The related work focuses on algorithms for community detection especially for co-authorship networks and how to track those detected communities over time.
 ``Most real world networks contain parts in which nodes are more highly connected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no widely accepted, unique definition.''~\cite{palla2005uncovering}
-The way ``more highly connected'' is preciesely defined makes the difference between community detection algorithms.
-It depends on the heuristic which is employed to identify communiteis.~\cite{porter2009communities}
+The way ``more highly connected'' is precisely defined makes the difference between community detection algorithms.
+It depends on the heuristic which is employed to identify communities.~\cite{porter2009communities}
 
 Fortunato~\cite{fortunato2010community} gives an extended overview about various types of community detection algorithms.
-To explain any would exceed the scope of this work.
-For example traditional methods include algorithms based on graph partitioning, hicharchical clustering and spectral clustering.
+To explain any, would exceed the scope of this work.
+For example, traditional methods include algorithms based on graph partitioning, hierarchical clustering and spectral clustering.
 There are also divisive and agglomerative algorithms.
-The best known one from this category is Girvan and Newman~\cite{girvan2002community}.
+The best-known one from this category is Girvan and Newman~\cite{girvan2002community}.
 
-Most algorihtms determine distinctive sets of communities, so a node can only belong to a single community.
-Most real world networks  consists of overlapping and nested communitiesm e.g.~friendship network of a person~\cite{palla2005uncovering}.
+Most algorithms determine distinctive sets of communities, so a node can only belong to a single community.
+Most real world networks consist of overlapping and nested communities e.g.~friendship network of a person~\cite{palla2005uncovering}.
 Fortunato~\cite{fortunato2010community} gives also an overview about algorithms detecting overlapping communities.
@@
 
-Not only overlapping communities exists in networks, but also communities are structured in an hirarchical way.
+Not only overlapping communities exists in networks, also communities are structured in an hierarchical way.
 Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015}, \cite{Cui201485} and~ \cite{Shen20091706}.
@@
 The clique percolation method (CPM) developed by Palla et~al.~\cite{palla2007quantifying} is used to identify overlapping communities in unweighted and undirected networks.
-The authors tested and evaluated their method using a co-authorship network, protein-protein interaction network, word associations network and a network constructed from variables within the source code of an open source ftp programm.
+The authors tested and evaluated their method using a co-authorship network, protein-protein interaction network, word associations network and a network constructed from variables within the source code of an open source FTP program.
 The following section explains the algorithm and summarizes the main findings of the paper regarding co-authorship networks.
 
-The underlying commmunity definition relies on the fact that a community consists of fully connected subgraphs, called \emph{cliques}.
+The underlying community definition relies on the fact that a community consists of fully connected subgraphs, called \emph{cliques}.
 \emph{$k$-cliques} are fully connected subgraphs with $k$ nodes.
@@
 The set of already found cliques do influence the found cliques in later steps, as the later found cliques are smaller.
-The detailed algorithm for step (2.1) finding cliques of size $s$ of $v$ can be looked up in supplemtary material to the paper on section 1.1.2, page 3.
+The detailed algorithm for step (2.1) finding cliques of size $s$ of $v$ can be looked up in supplementary material to the paper on section 1.1.2, page 3.
 The result of this step is a set with size $n_c$ of all maximal cliques, an example can be seen in figure~\ref{fig:3clique}.
@@
 	\includegraphics[width=0.8\textwidth]{matrix.png}
-		\caption{The clique-clique overlap matrix and the coresponding clique graph.
+		\caption{The clique-clique overlap matrix and the corresponding clique graph.
 The number inside the node is the number of nodes belonging to that community, the width of the edge represents the shared nodes.}
@@
 \subsubsection{(5) Post-processing.}
-The last setp of the algorithm assigns left over nodes, if possible, to communities.
-A node which is only connected to one certain community and is not part of a commnity already is assiciated with this community.
+The last step of the algorithm assigns left over nodes, if possible, to communities.
+A node which is only connected to one certain community and is not part of a community already is associated with this community.
 The number of nodes belonging to a community can be increased.
@@
 \label{cpm-construction}
-The edge weights are calculated with $$\frac{n}{n-1}$$ with $n$ beeing the number of authers per publication.
+The edge weights are calculated with $$\frac{n}{n-1}$$ with $n$ beeing the number of authors per publication.
 This results in modeling the collaboration between fewer authors as more intensive than the collaboration between a higher number of authors.  
-To generate an unweighted network all edges with an edgeweight below a certain threshold $w^*$ need to be removed, all others edgweights are replaced by weight $1$.
+To generate an unweighted network all edges with an edge weight below a certain threshold $w^*$ need to be removed, all others edge weight are replaced by weight $1$.
 Increasing $w^*$ results in fewer edges throughout the network, but stronger links and fewer detected communities.
 
-In addition a good $k$ needs to be chosen. When $k$ is increased the detected $k$-clique-communities shrink, but at the same time become more cohesive (stronger connected).
+In addition, a good $k$ needs to be chosen. When $k$ is increased the detected $k$-clique-communities shrink, but at the same time become more cohesive (stronger connected).
 So a good balance between $k$ and $w^*$ needs to be found resulting in a community structure which is highly structured.
@@
 The authors state that $k$ is usually between $3$ and $6$.
-If the number of links in a network are increased above some point a giant component evolves and covers the underlying community structure.
-So for each $k$ the treshold $w^*$ is lowered until the larges component becomes twice as big as the second largest component.
+If the number of links in a network is increased above some point a giant component evolves and covers the underlying community structure.
+So for each $k$ the threshold $w^*$ is lowered until the largest component becomes twice as big as the second largest component.
 For really choosing the best $k$ some further characteristics describing the community structure need to be investigated, see Supplementary Information of~\cite{palla2005uncovering} for more details.
@@
 $$C(A,B) = \frac{ \left| A \cap B\right| }{\left| A \cup B\right|}.$$
-As overlapping communities are allowed the matching from consecutive time steps in descending order of their relative node overlap can lead to missmatching.
-For example when small communities gain a lot of members or vice versa. An example for this problem is given in figure~X [TODO-PIC].
+As overlapping communities are allowed the matching from consecutive time steps in descending order of their relative node overlap can lead to mismatching.
+For example, when small communities gain a lot of members or vice versa. An example for this problem is given in figure~X [TODO-PIC].
 As a solution, for each time steps $t$ and $t+1$ a joint graph $g_{\cup}$ is constructed, containing all links from both networks.
@@
 For any community $D_i \in D$ or $E_j \in E$ exactly one community $V_k \in V$ can be found.
-For checking weather $E_i$ or $D_j$ is contained in $V_k$ the links are compared instead of nodes.
+For checking whether $E_i$ or $D_j$ is contained in $V_k$ the links are compared instead of nodes.
 For each community $V_i \in V$ the set of communities $D_i^k \in D$ and $E_j^k \in E$ contained in $V_i$ are extracted.
@@
 \subsubsection{Post-processing}
-In some cases a community which was disintegrated at a certain time step suddenly reappear in a later timestep, due to low publishing rates for example.
+In some cases, a community which was disintegrated at a certain time step suddenly reappears in a later timestep, due to low publishing rates for example.
 That means a newborn community includes a formerly dead community.
-This problem is overcome by just fillig the gap with the last step of the almost disintegrated community, this is calle gap-filling.
+This problem is overcome by just filling the gap with the last step of the almost disintegrated community, this is called gap-filling.
 
@@
 The social connection between people writing a paper together usually starts before the event and last for some time after the event.
-The higher the fequency the closer the relationship~\cite{ramasco2006social}.
+The higher the frequency the closer the relationship~\cite{ramasco2006social}.
 
-The edge weight resulting from one paper is $n/(n-1)$ with $n$ as thr number of authors. The edge weight between to nodes $a$ and $b$ at a certain time $t$ is calculated as
+The edge weight resulting from one paper is $n/(n-1)$ with $n$ as the number of authors. The edge weight between to nodes $a$ and $b$ at a certain time $t$ is calculated as
 
@@
 The event $i$ occurs at time $t_i$ and the corresponding edge weight at this time is called $w_i$.
-This decay function models the strenght of collaboration between authors over time considering all events ever occured in time.
+This decay function models the strength of collaboration between authors over time considering all events ever occurred in time.
 
-A threshold $w^*$ is used to only include certain edges to the temporal graph. So for each timestep a graph can be constructed based on the collaboration strenght per time step.
+A threshold $w^*$ is used to only include certain edges to the temporal graph. So for each timestep, a graph can be constructed based on the collaboration strength per time step.
 
@@
 No details about $\lambda$ is given in the paper.
-The data set used in the paper contained 142 month of publications. Details about data aggregation are not given, but looking at the figures it looks like 50 timeslices.
+The dataset used in the paper contained 142 months of publications. Details about data aggregation are not given, but looking at the figures it looks like 50 timeslices.
 
@@
 If members in small communities change frequently, they only live for a short time.
-Large communities live longer if members are changed permanently, if members stay the same they die quickly.
+Large communities live longer if members are changed permanently if members stay the same they die quickly.
 
@@
 
-It is nessesary to evaluate the quality of the resulting network after step (1) timeslicing, by looking at the basic statistics (number of publications per per timeslice, degree distribution, nodes on average per timeslice).
+It is necessary to evaluate the quality of the resulting network after step (1) time slicing, by looking at the basic statistics (number of publications per timeslice, degree distribution, nodes on average per timeslice).
 The function for calculating edge weights (2) could be taken from the paper (see section~\ref{evolution-constr}), but should be followed by checking if the resulting networks after step (3) are still valid.
-For finding the right $k$ (4) and $w^*$ (5) and extended analysis of network caracteristics like coverage of community structure and distribution if community size (see~\ref{evolution-vars}) would need to be carried out.
-Also the quality of the detected communities would need evaluation, comparing density within the community to outside the community.
+For finding the right $k$ (4) and $w^*$ (5) and extended analysis of network characteristics like coverage of community structure and distribution if community size (see~\ref{evolution-vars}) would need to be carried out.
+Also, the quality of the detected communities would need evaluation, comparing density within the community to outside the community.
 For step (1) CFinder or R could be used.
@@
 Determination of all cliques within a graph is a non-polynomial problem.
-The authos state that the required CPU time depends strongly on the structure of the input data, so no closed formula to estimate the system size depenance can be given.
-A complete CPM analysis for a co-authorship networl with $127.000$ links takes less than 2 hours on a PC\footnote{No details about the PC are given in the paper.}.
-I assume time complexity will not be a problem because my dataset contains $18.404$ eges in total, when not applying any threshold.
+The authors state that the required CPU time depends strongly on the structure of the input data, so no closed formula to estimate the system size dependence can be given.
+A complete CPM analysis for a co-authorship network with $127.000$ links takes less than 2 hours on a PC\footnote{No details about the PC are given in the paper.}.
+I assume time complexity will not be a problem because my dataset contains $18.404$ edges in total, when not applying any threshold.
 
 \section{Future Work}
-As this paper dicusses only one popular method, an extensive literature research should follow, finding out more methods solving the problem.
-Also a closer look at more recent work would be nesessary.
+As this paper discusses only one popular method, an extensive literature research should follow, finding out more methods solving the problem.
+Also, a closer look at more recent work would be necessary.
 It would be also interesting to find a good model for calculating edge weights with respect to scientific collaboration definitions.
-The visuaization of the community evolution remains open and would be a broad topic, but exciting to investigate further.
+The visualization of the community evolution remains open and would be a broad topic, but exciting to investigate further.
 

### 2016-01-02 paper/paper.tex
bg for itemize
new pics and some stuff

@@
 \usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{caption}
+
 \usepackage{url}
@@
 \renewcommand*\familydefault{\sfdefault}
+
+\usepackage{xcolor}
+\definecolor{usethiscolorhere}{rgb}{0.85,0.85,0.85}
 
@@
 \begin{figure}
-	\includegraphics[width=\textwidth]{villsize.jpg}
-	\caption{lifetime of a community}
+	\includegraphics[width=\textwidth]{img/fullSizeEvolution.jpg}
+	\caption{Lifetime of a community, from~[9]}
 	\label{fig:evolution}
@@
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{3-clique}
-        \caption{3-cliquel}
-        \label{fig:3clique}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{4-clique}
-        \caption{4-clique}
-        \label{fig:4clique}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{cliqueinside}
-        \caption{4-clique inside a graph}
-        \label{fig:cliqueInside}
-    \end{subfigure}
-    \caption{Examle of cliques}\label{fig:cliques}
+	\includegraphics[width=\textwidth]{img/cliques.png}
+    \caption{Examples for a $3$-clique, $4$-clique and a $4$-clique inside a graph.}
+    \label{fig:cliques}
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[width=\textwidth]{rolling.png}
+	\includegraphics[width=\textwidth]{img/rolling.png}
 	\caption{Template rolling for a $3$-clique}
@@
 Based on the explained community definition the algorithm consists of the following steps:
+
+\medskip
+
+\noindent
+\colorbox{usethiscolorhere}{
+\begin{minipage}{\dimexpr\textwidth-2\fboxsep}
 
@@
 
+\end{minipage}
+}
+
 \subsubsection{(1) Find all maximal cliques}
@@
 That is why they are detected in decreasing order of their size.
-The largest possible clique size $s_{max}$ is determinde by the maximal degree $d_{max}$ found in the network.
+The largest possible clique size $s_{max}$ is determinde by the maximal degree $d_{max}$ found in the network. The following steps describe the algorithm for finding maximal cliques:
+
+\medskip
+
+\noindent
+\colorbox{usethiscolorhere}{
+\begin{minipage}{\dimexpr\textwidth-2\fboxsep}
 
@@
 
+\end{minipage}
+}
+
+\medskip
+
 The set of already found cliques do influence the found cliques in later steps, as the later found cliques are smaller.
 The detailed algorithm for step (2.1) finding cliques of size $s$ of $v$ can be looked up in supplementary material to the paper on section 1.1.2, page 3.
-The result of this step is a set with size $n_c$ of all maximal cliques, an example can be seen in figure~\ref{fig:3clique}.
+The result of this step is a set of size $n_c$ containing all maximal cliques, an example can be seen in figure~\ref{fig:allmaxcliques}.
 
@@
 \begin{center}
-	\includegraphics[width=0.8\textwidth]{allmaxcliques.png}
-		\caption{All maximal cliques in a graph. Each color represents a maximal clique.}
+	\includegraphics[width=0.8\textwidth]{img/allmaxcliques.png}
+		\caption{All maximal cliques in a graph. Each color represents a maximal clique. Adapted from~[9].}
 		\label{fig:allmaxcliques}
@@
 \begin{center}
-	\includegraphics[width=0.8\textwidth]{matrix.png}
+	\includegraphics[width=0.8\textwidth]{img/matrix.png}
 		\caption{The clique-clique overlap matrix and the corresponding clique graph.
@@
 \begin{center}
-	\includegraphics[width=0.8\textwidth]{matrixtrashed}
-		\caption{This is the resulting clique graph after the thresholding with $k=4$. All connected components do represent a $k$-clique-community. In this example are two communities.}
+	\includegraphics[width=0.8\textwidth]{img/matrixtrashed}
+		\caption{This is the resulting clique graph after thresholding with $k=4$. All connected components do represent a $k$-clique-community. In this example two communities exist.}
 		\label{fig:matrixtrashed}
@@
 
-\subsection{Construction of the co-authorship network}
+\subsection{Construction of the Co-Authorship Network}
 \label{cpm-construction}
@@
 
-\subsection{Main Findings of the paper}
+\subsection{Main Findings of the Paper}
 Overlaps in networks are significant.
@@
 In general, the algorithm uses the clique percolation method to find communities in each temporal graph, and after that matches the communities of consecutive timesteps.
+
+\medskip
+
+\noindent
+\colorbox{usethiscolorhere}{
+\begin{minipage}{\dimexpr\textwidth-2\fboxsep}
 
@@
 
-The following describes steps (2) and (3) in detail.
+\end{minipage}
+}
+
+\medskip
+
+The following describes steps (2) Matching Communities and (3) Post-Processing in detail.
 Step (1) was already explained in section~\ref{cpm}.
@@
 As overlapping communities are allowed the matching from consecutive time steps in descending order of their relative node overlap can lead to mismatching.
-For example, when small communities gain a lot of members or vice versa. An example for this problem is given in figure~X [TODO-PIC].
+For example, when small communities gain a lot of members or vice versa. An example for this problem is given in figure~\ref{fig:mismatch}.
 As a solution, for each time steps $t$ and $t+1$ a joint graph $g_{\cup}$ is constructed, containing all links from both networks.
@@
 For each community $V_i \in V$ the set of communities $D_i^k \in D$ and $E_j^k \in E$ contained in $V_i$ are extracted.
-Now the relative node overlap between every possible pair can be calculated as with
+Now the relative node overlap between every possible pair can be calculated with
 $$C^k_{i,j} = \frac{\left| D_i^k \cap E_j^k\right|}{\left| D_i^k\cup E_j^k \right| }$$
@@
 
-In figures~X three examples are given: figXa is a simple matching of a propagating community, figXb showing two merging communities with one community dying and figXc showing the splitting of a community into two communities with one community is born.
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.8\textwidth]{img/mismatch.png}
+		\caption{Example for mismatching communities in consecutive timesteps.
+$A$(green) and $B$(blue) are two communities, red nodes belong to both communities.
+The overlap between $A_t$ and $B_{t+1}$ is bigger than between $A_t$ and $A_{t+1}$}.
+		\label{fig:mismatch}
+\end{center}
+\end{figure}
 
-\subsubsection{Post-processing}
+\subsubsection{Post-Processing}
 In some cases, a community which was disintegrated at a certain time step suddenly reappears in a later timestep, due to low publishing rates for example.
@@
 
-\subsection{Construction of the temporal co-authorship networks}
+\subsection{Construction of the Temporal Co-Authorship Networks}
 \label{evolution-constr}
@@
 
-\subsection{Main Findings of the paper}
+\subsection{Main Findings of the Paper}
 \label{evolution-findings}
@@
 This part describe the steps I would need to undertake to carry out a temporal analysis of communities within the geochemistry data set or with any other data set, which forms a collaboration network.
+
+\medskip
+
+\noindent
+\colorbox{usethiscolorhere}{
+\begin{minipage}{\dimexpr\textwidth-2\fboxsep}
 
@@
 
+\end{minipage}
+}
+
+\medskip
+
 It is necessary to evaluate the quality of the resulting network after step (1) time slicing, by looking at the basic statistics (number of publications per timeslice, degree distribution, nodes on average per timeslice).
 The function for calculating edge weights (2) could be taken from the paper (see section~\ref{evolution-constr}), but should be followed by checking if the resulting networks after step (3) are still valid.
-For finding the right $k$ (4) and $w^*$ (5) and extended analysis of network characteristics like coverage of community structure and distribution if community size (see~\ref{evolution-vars}) would need to be carried out.
+For finding the right $k$ (4) and $w^*$ (5) and extended analysis of network characteristics like coverage of community structure and distribution if community size would need to be carried out.
 Also, the quality of the detected communities would need evaluation, comparing density within the community to outside the community.

### 2016-01-02 paper/paper.tex
last img

@@
 \subsubsection{(4) Each connected component in the clique graph form a $k$-clique-community.}
-In the resulting graph we need to look for connected components, those represent the $k$-clique-communities, see figure~\ref{fig:result}.
+In the resulting graph we need to look for connected components, those represent the $k$-clique-communities, see figure~\ref{fig:final}.
 
@@
 \begin{center}
-	\includegraphics[width=0.8\textwidth]{result}
+	\includegraphics[width=0.8\textwidth]{img/final}
 		\caption{Here the two resulting $k$-clique-communities are shown.}
-		\label{fig:result}
+		\label{fig:final}
 \end{center}

### 2016-01-11 paper/paper.tex
finale version

@@
 \begin{abstract}
-Detection of overlapping communities plays an important role when it comes to analyzing scientific collaboration using social networks.
-This paper focuses on describing a method to analyze the temporal development of overlapping communities within co-authorship networks.
-The paper mainly relies on the work of Palla~et~al.
-using the clique percolation method for community extraction.
-The main goal was to find and understand an appropriate algorithm, which can be applied to an existing dataset of scientific publications.
-Implications regarding further actions and time complexity are discussed.
+Detection of overlapping communities plays an important role when it comes to analysing scientific collaboration using social networks.
+The present paper describes a method to analyse the temporal development of overlapping communities within co-authorship networks.
+The paper mainly relies on the clique percolation method for community extraction.
+propounded by Palla~et~al.
+The main goal is to find and understand an appropriate algorithm, that can be applied to an existing dataset of scientific publications.
+Implications for further actions and time complexity are discussed.
 
@@
 \section{Introduction and Motivation}
-A \emph{social network} is a representation of a social structure consisting of actors, e.g.~individuals, affiliations, and their social interactions.
-The network model conceptualizes e.g.~social, economic or political structures as lasting patterns of interactions between actors.~\cite{wasserman1994social}
+A \emph{social network} is a representation of a social structure comprising actors such as individuals, affiliations, as well as their social interactions.
+The network model conceptualizes social, economic, or political structures as lasting patterns of interactions between actors.~\cite{wasserman1994social}
 
-A \emph{co-authorship network} is a scientific collaboration network, where actors are scientists and the social interaction is collaboration work resulting in publishing papers together.
-In mathematical terms networks are graphs, therefore they consist of nodes (vertex) and links (edges).
-In a co-authorship network nodes are individual authors who are considered connected if they co-authored a paper.~\cite{newman2001structure}
+A \emph{co-authorship network} is a scientific collaboration network, with scientists as actors, where the social interaction leads to collaborative papers.
+In mathematical terms, networks are graphs, and thus consist of nodes (vertex) and links (edges).
+In a co-authorship network, nodes are individual authors who are considered connected if they co-author a paper.~\cite{newman2001structure}
 
-Usually, those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different network measurements, detection and evolution of communities and many more.
+Usually, those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different network measurements, detection and evolution of communities, and more.
 See~\cite{barabasi2002evolution}, \cite{newman2001structure} and \cite{newman2004coauthorship} for more details.
 
-This seminar paper is motivated by a dataset consisting of $2.277$ publications related to geochemistry focusing on papers talking about stable metal isotopes (e.g.~potassium, magnesium, lithium, silicon).
-This data was used to build a cummulated co-authorship network using an very simple approach to model collaboration.
+This seminar paper is motivated by a dataset of $2.277$ publications related to geochemistry focusing on papers talking about stable metal isotopes (e.g.~potassium, magnesium, lithium, silicon, etc.).
+This data was used to build a cumulated co-authorship network using a simple approach to model collaboration.
 
-The dataset was collected using the bibliographic database scopus\footnote{\url{http://www.scopus.com/}} and includes publications starting from 1997/98 until 2014.
-The dataset consists of authors, co-authors, title, year, abstract and affiliations.
-A basic network analysis had already been conducted for example centrality measurement, community detection, degree distribution and average degree.
+The dataset was collected using the bibliographic database scopus\footnote{\url{http://www.scopus.com/}, accessed: March 2014} and includes publications starting from 1997/98 until 2014.
+The dataset comprised of authors, co-authors, title, year, abstract and affiliations.
+A basic network analysis has already been performed regarding such aspects as centrality measurement, community detection, degree distribution, and average degree.
 
-As the data set includes temporal information~(publishing year), the following question arises: How do communities within this type of co-authorship network evolve over time?
-In geochemistry people often tend to focus on one isotope system, and stick to this topic for a long time.
-Do researchers in geochemistry really focus on one specific topic or do they change the field over time?
+Since the dataset includes temporal information~(publishing year), the following question arises: How do communities within this type of co-authorship network evolve over time?
+In geochemistry, people often tend to focus on one isotope system and stick to this topic for a long time.
+Do researchers in geochemistry really focus on one specific topic or change the field over time?
 
-The goal of this seminar paper therefor is to find and explain an already established and well-understood method for analyzing the temporal development of communities within co-authorship networks.
-The main point is to understand the underlying algorithm in detail and to find out implications and challenges when applying this method to the geochemistry dataset.
+Therefore, this seminar paper aims is to find and explain an already established and well-understood method for analysing the temporal development of communities within co-authorship networks.
+The main point is to understand the underlying algorithm in detail, and to find out implications and challenges when applying this method to the geochemistry dataset.
 
@@
 \label{related}
-The related work focuses on algorithms for community detection especially for co-authorship networks and how to track those detected communities over time.
+The related work focuses on algorithms for community detection especially for co-authorship networks and seeks to track those detected communities over time.
 ``Most real world networks contain parts in which nodes are more highly connected to each other than to the rest of the network, those sets are usually called clusters, communities, cohesive groups or modules, they have no widely accepted, unique definition.''~\cite{palla2005uncovering}
-The way ``more highly connected'' is precisely defined makes the difference between community detection algorithms.
-It depends on the heuristic which is employed to identify communities.~\cite{porter2009communities}
+The precision with which ``more highly connected'' is defined makes the difference between community detection algorithms.
+It depends on the heuristic that is employed to identify communities.~\cite{porter2009communities}
 
-Fortunato~\cite{fortunato2010community} gives an extended overview about various types of community detection algorithms.
-To explain any, would exceed the scope of this work.
-For example, traditional methods include algorithms based on graph partitioning, hierarchical clustering and spectral clustering.
+Fortunato~\cite{fortunato2010community} gives an extended overview of the various types of community detection algorithms.
+Explaining any of those would be beyond the scope of this work.
+For example, traditional methods include algorithms based on graph partitioning, hierarchical clustering, and spectral clustering.
 There are also divisive and agglomerative algorithms.
@@
 Most algorithms determine distinctive sets of communities, so a node can only belong to a single community.
-Most real world networks consist of overlapping and nested communities e.g.~friendship network of a person~\cite{palla2005uncovering}.
-Fortunato~\cite{fortunato2010community} gives also an overview about algorithms detecting overlapping communities.
-The best known and widely cited is the \emph{clique percolation method (CPM)} by Palla et~al.~\cite{palla2005uncovering}.
-There is an implementation provided by the authors, called \emph{CFinder}\footnote{CFinder is a tool which implements the clique percolation method by Palla and finding and visualizing overlapping dense groups of nodes in networks.
-\url{http://www.cfinder.org/}, 05.12.2015, 22:43}, and an implementation in the R igraph library\footnote{\url{http://igraph.wikidot.com/community-detection-in-r#toc0}, 05.12.2015, 22:45}.
+Most realworld networks consist of overlapping and nested communities, e.g.~friendship network of a person~\cite{palla2005uncovering}.
+Fortunato~\cite{fortunato2010community} also gives an overview of algorithms detecting overlapping communities.
+The best known and widely cited of these is the \emph{clique percolation method (CPM)} by Palla et~al.~\cite{palla2005uncovering}.
+There is an implementation provided by the authors, called \emph{CFinder}\footnote{CFinder is a tool that implements the clique percolation method by Palla.
+It finds and visualizes overlapping dense groups of nodes in networks.
+\url{http://www.cfinder.org/}, accessed: 05.12.2015}, as well as one in the R igraph library\footnote{\url{http://igraph.wikidot.com/community-detection-in-r#toc0}, accessed: 05.12.2015}.
 
-Not only overlapping communities exists in networks, also communities are structured in an hierarchical way.
-Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015}, \cite{Cui201485} and~ \cite{Shen20091706}.
+Not only do overlapping communities exist in networks, but communities are also structured in a hierarchical manner.
+Recent work on algorithms detecting hierarchicla and overlapping structures  include~\cite{1367-2630-11-3-033015}, \cite{Cui201485} and~ \cite{Shen20091706}.
 
@@
 The detection of dynamic communities has been studied by Palla et~al.~\cite{palla2007quantifying} using CPM for each snapshot of the graph.
-Further information on dynamic communities can be found in section 13 of~\cite{fortunato2010community}.
+Further information on dynamic communities can be found in Section 13 of~\cite{fortunato2010community}.
 
@@
 
-As CPM is a widely used method for detecting overlapping communities I will explain this method in more detail.
-The following sections describe the CPM and also the temporal algorithm mainly based on the two papers of Palla et~al.~\cite{palla2005uncovering} and~\cite{palla2007quantifying}.
+Since CPM is a widely used method for detecting overlapping communities I will explain this method in more detail.
+The following sections describe the CPM as wll as the temporal algorithm based on two papers by Palla et~al.~\cite{palla2005uncovering} and~\cite{palla2007quantifying}.
 
@@
 \label{cpm}
-The clique percolation method (CPM) developed by Palla et~al.~\cite{palla2007quantifying} is used to identify overlapping communities in unweighted and undirected networks.
-The authors tested and evaluated their method using a co-authorship network, protein-protein interaction network, word associations network and a network constructed from variables within the source code of an open source FTP program.
+The clique percolation method (CPM), developed by Palla et~al.~\cite{palla2007quantifying}, is used to identify overlapping communities in unweighted and undirected networks.
+The authors tested and evaluated their method using a co-authorship network, protein-protein interaction network, word association networks and a network constructed from variables within the source code of an open-source FTP program.
 The following section explains the algorithm and summarizes the main findings of the paper regarding co-authorship networks.
 
-The underlying community definition relies on the fact that a community consists of fully connected subgraphs, called \emph{cliques}.
+The underlying community definition relies on the fact that a community comprises fully connected subgraphs, called \emph{cliques}.
 \emph{$k$-cliques} are fully connected subgraphs with $k$ nodes.
-In figure~\ref{fig:cliques} an example of $\{3,4\}$-cliques are given.
+In Figure~\ref{fig:cliques}, an example of $\{3,4\}$-cliques are given.
 A community, in this context, is called a \emph{$k$-clique-community}, which is defined as a union of all $k$-cliques, which can be reached from each other through a number of \emph{adjacent $k$-cliques}.
 Two $k$-cliques are called adjacent if they share $k-1$ nodes.
-In figure~\ref{fig:rolling} the so called $k$-clique template rolling is visualized for a $3$-clique.
-A $k$-clique-community is best described by relocating one node until all nodes of the community are discovered.
+In Figure~\ref{fig:rolling}, the so-called $k$-clique template rolling is visualized for a $3$-clique.
+A $k$-clique-community is best described by relocating one node until all the nodes of the community are discovered.
 
@@
 \label{cpm-algo}
-The starting point for the algorithm is an undirected and unweighted graph. In section \ref{cpm-construction} we talk about generating the  unweighted co-authorship graph.
-Based on the explained community definition the algorithm consists of the following steps:
+The starting point for the algorithm is an undirected and unweighted graph. In Section \ref{cpm-construction}, we talk about generating the unweighted co-authorship graph.
+Based on the explained community definition, the algorithm consists of the following steps:
 
@@
 \item[(3)] Threshold the matrix with a certain $k$.
-\item[(4)] Each connected component in the clique graph form a $k$-clique-community.
+\item[(4)] Each connected component in the clique graph forms a $k$-clique-community.
 \item[(5)] Post-processing.
@@
 Instead of finding all $k$-cliques, as a first step, the algorithm searches for all maximal cliques.
-Instead of finding all $k$-cliques, which is a polynomial problem, his can be done in exponential time the authors state.
-Maximal cliques cannot be subsets of larger cliques.
-That is why they are detected in decreasing order of their size.
-The largest possible clique size $s_{max}$ is determinde by the maximal degree $d_{max}$ found in the network. The following steps describe the algorithm for finding maximal cliques:
+Instead of finding all $k$-cliques, which is a polynomial problem, this can be done in exponential time, state the authors.
+Maximal cliques cannot be subsets of larger cliques, which is why they are detected in decreasing order of their size.
+The largest possible clique size $s_{max}$ is determined by the maximal degree $d_{max}$ found in the network. The following steps describe the algorithm for finding maximal cliques:
 
@@
 
-The set of already found cliques do influence the found cliques in later steps, as the later found cliques are smaller.
-The detailed algorithm for step (2.1) finding cliques of size $s$ of $v$ can be looked up in supplementary material to the paper on section 1.1.2, page 3.
-The result of this step is a set of size $n_c$ containing all maximal cliques, an example can be seen in figure~\ref{fig:allmaxcliques}.
+The set of already found cliques influence the found cliques in later steps, as the later found cliques are smaller.
+The detailed algorithm for the step (2.1) to find cliques of size $s$ of $v$ can be looked up in the supplementary material of the paper in Section 1.1.2, page 3.
+The result of this step is a set of size $n_c$ containing all maximal cliques, an example of which can be seen in Figure~\ref{fig:allmaxcliques}.
 
@@
 	\includegraphics[width=0.8\textwidth]{img/allmaxcliques.png}
-		\caption{All maximal cliques in a graph. Each color represents a maximal clique. Adapted from~[9].}
+		\caption{All maximal cliques in a graph. Each colour represents a maximal clique. Adapted from~[9].}
 		\label{fig:allmaxcliques}
@@
 
-\subsubsection{(2) Prepare clique-clique overlap matrix, or clique graph}
-The dimension of the overlap matrix is $n_c \times n_c$. Each row and column represent a clique.
+\subsubsection{(2) Prepare clique- clique overlap matrix, or clique graph}
+The dimension of the overlap matrix is $n_c \times n_c$.
+Each row and column represents a clique.
 All non-diagonal matrix elements represent the number of nodes those cliques share.
@@
 This matrix is only generated once.
-In figure~\ref{fig:matrix} the clique-clique overlap matrix of the graph of figure~\ref{fig:allmaxcliques} and the coressponding clique graph is shown.
+In Figure~\ref{fig:matrix}, the clique- clique overlap matrix of the graph in Figure~\ref{fig:allmaxcliques} and the corresponding clique graph is shown.
 
@@
 	\includegraphics[width=0.8\textwidth]{img/matrix.png}
-		\caption{The clique-clique overlap matrix and the corresponding clique graph.
+		\caption{The clique- clique overlap matrix and the corresponding clique graph.
 The number inside the node is the number of nodes belonging to that community, the width of the edge represents the shared nodes.}
@@
 The remaining elements are set to $1$, resulting in a binary matrix, representing a network of cliques.
-The thresholding can be done repeatedly without calculating a new matrix, see figure~\ref{fig:matrixtrashed}.
+The thresholding can be done repeatedly without calculating a new matrix.
+See Figure~\ref{fig:matrixtrashed}.
 
@@
 	\includegraphics[width=0.8\textwidth]{img/matrixtrashed}
-		\caption{This is the resulting clique graph after thresholding with $k=4$. All connected components do represent a $k$-clique-community. In this example two communities exist.}
+		\caption{This is the resulting clique graph after thresholding with $k=4$. All connected components represent a $k$-clique- community. There are two communities in this example.}
 		\label{fig:matrixtrashed}
@@
 
-\subsubsection{(4) Each connected component in the clique graph form a $k$-clique-community.}
-In the resulting graph we need to look for connected components, those represent the $k$-clique-communities, see figure~\ref{fig:final}.
+\subsubsection{(4) Each connected component in the clique graph forms a $k$-clique- community.}
+In the resulting graph, we need to look for connected components that represent the $k$-clique- communities, see Figure~\ref{fig:final}.
 
 \subsubsection{(5) Post-processing.}
-The last step of the algorithm assigns left over nodes, if possible, to communities.
-A node which is only connected to one certain community and is not part of a community already is associated with this community.
+The last step of the algorithm assigns leftover nodes, if possible, to communities.
+A node which is only connected to one particular community and is not part of a community is associated with this community.
 The number of nodes belonging to a community can be increased.
@@
 	\includegraphics[width=0.8\textwidth]{img/final}
-		\caption{Here the two resulting $k$-clique-communities are shown.}
+		\caption{Here the two resulting $k$-clique- communities are shown.}
 		\label{fig:final}
@@
 \label{cpm-construction}
-The edge weights are calculated with $$\frac{n}{n-1}$$ with $n$ beeing the number of authors per publication.
-This results in modeling the collaboration between fewer authors as more intensive than the collaboration between a higher number of authors.  
-To generate an unweighted network all edges with an edge weight below a certain threshold $w^*$ need to be removed, all others edge weight are replaced by weight $1$.
+The edge weights are calculated with $$\frac{n}{n-1}$$, with $n$ being the number of authors per publication.
+This leads to modelling the collaboration between fewer authors as more intensive than the collaboration between a higher number of authors.  
+To generate an unweighted network, all edges with an edge weight below a certain threshold $w^*$ need to be removed.
+All other edge weights are replaced by weight $1$.
 Increasing $w^*$ results in fewer edges throughout the network, but stronger links and fewer detected communities.
 
-In addition, a good $k$ needs to be chosen. When $k$ is increased the detected $k$-clique-communities shrink, but at the same time become more cohesive (stronger connected).
-So a good balance between $k$ and $w^*$ needs to be found resulting in a community structure which is highly structured.
+Additionally, a good $k$ needs to be chosen. When $k$ is increased, the detected $k$-clique- communities shrink, but at the same time they become more cohesive (stronger connected).
+So a good balance between $k$ and $w^*$ needs to be found to obtain a highly structured community.
 
 The authors state that $k$ is usually between $3$ and $6$.
-If the number of links in a network is increased above some point a giant component evolves and covers the underlying community structure.
-So for each $k$ the threshold $w^*$ is lowered until the largest component becomes twice as big as the second largest component.
-For really choosing the best $k$ some further characteristics describing the community structure need to be investigated, see Supplementary Information of~\cite{palla2005uncovering} for more details.
+If the number of links in a network is increased above a certain point, a giant component evolves and covers the underlying community structure.
+Therefore, for each $k$, the threshold $w^*$ is lowered until the largest component becomes twice as big as the second-largest component.
+To choose the best $k$, some further characteristics describing the community structure need to be investigated.
+See supplementary information of~\cite{palla2005uncovering} for more details.
 
@@
 Overlaps in networks are significant.
-The distributions introduced in the paper (community size, community degree, overlap size, membership number) reveal universal features of networks.
+The distributions introduced in the paper (community size, community degree, overlap size, and membership number) reveal universal features of networks.
 The network of communities has non-trivial correlations and specific scaling properties.~\cite{palla2005uncovering}
@@
 \label{evolution}
-Palla et~al.~\cite{palla2007quantifying} developed an algorithm based on clique percolation (see section~\ref{cpm}) that allows the investigation of overlapping communities over time.
-They uncovered basic relationships characterizing community evolution within a co-authorship network and a phone-call network.
+Palla et~al.~\cite{palla2007quantifying} developed an algorithm based on clique percolation (see Section~\ref{cpm}) that allows the investigation of overlapping communities over time.
+They uncovered basic relationships that characterize community evolution within a co-authorship network and a phone-call network.
 The following section describes the main steps of the algorithm.
-A short summary of their main findings can be found in section~\ref{evolution-findings}.
+A short summary of their main findings can be found in Section~\ref{evolution-findings}.
 
@@
 \label{evolution-algo}
-The starting point of the algorithm is an undirected and unweighted graph for each timestep.
-The construction of those temporal graphs is explained in section~\ref{evolution-constr}.
-In general, the algorithm uses the clique percolation method to find communities in each temporal graph, and after that matches the communities of consecutive timesteps.
+The starting point of the algorithm is an undirected and unweighted graph for each time step.
+The construction of those temporal graphs is explained in Section~\ref{evolution-constr}.
+In general, the algorithm uses the clique percolation method to find communities in each temporal graph, and subsequently matches the communities of consecutive time steps.
 
@@
 			\item Calculate relative overlap for each pair.
-			\item Match communities in decending order.
+			\item Match communities in descending order.
 		\end{itemize}
@@
 
-The following describes steps (2) Matching Communities and (3) Post-Processing in detail.
-Step (1) was already explained in section~\ref{cpm}.
+The following section describes the steps (2) Matching Communities and (3) Post-Processing in detail.
+Step (1) was already explained in Section~\ref{cpm}.
 
@@
 \label{evolution-algo-matching}
-For matching communities, the \emph{relative node overlap} $C(A,B)$ between two nodes $A$ and $B$, in a simple way, is defined as
+For matching communities, the \emph{relative node overlap} $C(A,B)$ between the nodes $A$ and $B$, is defined simply as
 $$C(A,B) = \frac{ \left| A \cap B\right| }{\left| A \cup B\right|}.$$
-As overlapping communities are allowed the matching from consecutive time steps in descending order of their relative node overlap can lead to mismatching.
-For example, when small communities gain a lot of members or vice versa. An example for this problem is given in figure~\ref{fig:mismatch}.
-As a solution, for each time steps $t$ and $t+1$ a joint graph $g_{\cup}$ is constructed, containing all links from both networks.
-Let $D$ be the set of communities at time step $t$ and $E$ the set of communities at time step $t+1$. The set of communities from the joint graph $g_{\cup}$ are extracted using CPM and are called $V$.
-For any community $D_i \in D$ or $E_j \in E$ exactly one community $V_k \in V$ can be found.
-For checking whether $E_i$ or $D_j$ is contained in $V_k$ the links are compared instead of nodes.
-For each community $V_i \in V$ the set of communities $D_i^k \in D$ and $E_j^k \in E$ contained in $V_i$ are extracted.
+As overlapping communities are allowed, the matching from consecutive time steps in descending order of their relative node overlap can lead to mismatching, such as when small communities gain a lot of members or vice versa.
+An example for this problem is given in Figure~\ref{fig:mismatch}.
+As a solution, for each of the time steps $t$ and $t+1$, a joint graph $g_{\cup}$ is constructed, that contains all links from both networks.
+Let $D$ be the set of communities at time step $t$, and $E$ the set of communities at time step $t+1$.
+The set of communities from the joint graph $g_{\cup}$ are extracted using CPM and are called $V$.
+For any community $D_i \in D$ or $E_j \in E$, exactly one community $V_k \in V$ can be found.
+To check whether $E_i$ or $D_j$ is contained in $V_k$, the links are compared instead of nodes.
+For each community $V_i \in V$, the sets of communities $D_i^k \in D$ and $E_j^k \in E$ contained in $V_i$ are extracted.
 Now the relative node overlap between every possible pair can be calculated with
@@
 	\includegraphics[width=0.8\textwidth]{img/mismatch.png}
-		\caption{Example for mismatching communities in consecutive timesteps.
-$A$(green) and $B$(blue) are two communities, red nodes belong to both communities.
-The overlap between $A_t$ and $B_{t+1}$ is bigger than between $A_t$ and $A_{t+1}$}.
+		\caption{Example of mismatching communities in consecutive time steps.
+$A$(green) and $B$(blue) are two communities.
+Red nodes belong to both communities.
+The overlap between $A_t$ and $B_{t+1}$ is bigger than that between $A_t$ and $A_{t+1}$}.
 		\label{fig:mismatch}
@@
 \subsubsection{Post-Processing}
-In some cases, a community which was disintegrated at a certain time step suddenly reappears in a later timestep, due to low publishing rates for example.
-That means a newborn community includes a formerly dead community.
-This problem is overcome by just filling the gap with the last step of the almost disintegrated community, this is called gap-filling.
+In some cases, a community that was disintegrated at a certain time step suddenly reappears in a later time step due to low publishing rates, for example.
+This means a newborn community includes a dead community.
+This problem is overcome by just filling the gap with the last step of the almost disintegrated community, which is called gap filling.
 
@@
 Events in the co-authorship network are publications.
-The social connection between people writing a paper together usually starts before the event and last for some time after the event.
-The higher the frequency the closer the relationship~\cite{ramasco2006social}.
+The social contract between people writing a paper together usually starts before the event and lasts for some time after the event.
+The higher the frequency, the closer the relationship~\cite{ramasco2006social}.
 
-The edge weight resulting from one paper is $n/(n-1)$ with $n$ as the number of authors. The edge weight between to nodes $a$ and $b$ at a certain time $t$ is calculated as
+The edge weight resulting from one paper is $n/(n-1)$ with $n$ as the number of authors.
+The edge weight between the nodes $a$ and $b$ at a certain time $t$ is calculated as
 
@@
 
-The summation runs over all collaboration event in which $a$ and $b$ are involved.
+The summation runs over all collaborative events in which $a$ and $b$ are involved.
 The event $i$ occurs at time $t_i$ and the corresponding edge weight at this time is called $w_i$.
-This decay function models the strength of collaboration between authors over time considering all events ever occurred in time.
+Considerinh all events ever occurred in time, this decay function models the strength of the collaboration between authors over time.
 
-A threshold $w^*$ is used to only include certain edges to the temporal graph. So for each timestep, a graph can be constructed based on the collaboration strength per time step.
+A threshold $w^*$ is used to include only certain edges in the temporal graph. Hence, for each time step, a graph can be constructed based on the collaboration strength per time step.
 
 The authors of the paper used $w^*=1.0$ for the co-authorship network.
-No details about $\lambda$ is given in the paper.
-The dataset used in the paper contained 142 months of publications. Details about data aggregation are not given, but looking at the figures it looks like 50 timeslices.
+The paper gives no details about $\lambda$.
+The dataset used in the paper contained 142 months of publications. Details of data aggregation are not provided. However, with respect to figures, it appears to be 50 time slices.
 
@@
 The paper summarized differences between large and small communities and their development over time.
-Small communities live longer if their members stay the same over time.
-If members in small communities change frequently, they only live for a short time.
-Large communities live longer if members are changed permanently if members stay the same they die quickly.
+Small communities live longer if their members remain unchanged over time.
+If members in small communities change frequently, they live only for a short time.
+Large communities live longer if members are changed permanently; if the members remain the same, they die quickly.
 
 \section{Implications and Efficiency of the Algorithm}
-This part describe the steps I would need to undertake to carry out a temporal analysis of communities within the geochemistry data set or with any other data set, which forms a collaboration network.
+This part describes the steps I would need to undertake to carry out a temporal analysis of communities within the geochemistry dataset or within any other dataset, that forms a collaboration network.
 
@@
 \small
-	\item[(1)] Genrate slices of the network for each year.
+	\item[(1)] Generate slices of the network for each year.
 	\item[(2)] Find function for calculating edge weights.
@@
 	\item[(4)] Find out $k$.
-	\item[(5)] Adjust treshold $w^*$ according to $k$.	
+	\item[(5)] Adjust threshold $w^*$ according to $k$.	
 	\item[(6)] Do CPM for each snapshot.
@@
 
-It is necessary to evaluate the quality of the resulting network after step (1) time slicing, by looking at the basic statistics (number of publications per timeslice, degree distribution, nodes on average per timeslice).
-The function for calculating edge weights (2) could be taken from the paper (see section~\ref{evolution-constr}), but should be followed by checking if the resulting networks after step (3) are still valid.
-For finding the right $k$ (4) and $w^*$ (5) and extended analysis of network characteristics like coverage of community structure and distribution if community size would need to be carried out.
-Also, the quality of the detected communities would need evaluation, comparing density within the community to outside the community.
-For step (1) CFinder or R could be used.
-It is open to me if there is an implementation for the community mapping (7), if not this step would need to be implemented.
+It is necessary to evaluate the quality of the resulting network after step (1) time slicing, by looking at the basic statistics (number of publications per time slice, degree distribution, average nodes per time slice).
+The function for calculating edge weights (2) could be taken from the paper (see Section~\ref{evolution-constr}), but it should be checked if the resulting networks after step (3) are still valid.
+To find the right $k$ (4) and $w^*$ (5) the analysis of network characteristics like coverage of community structure and distribution if community size needs to be extended.
+Moreover, the quality of the detected communities would need evaluation when the density within the community is compared to with outside the community.
+For step (1), CFinder or R could be used.
+I am open to the idea of implementation for the community mapping (7). If there were none, this step would need to be implemented.
 
-Determination of all cliques within a graph is a non-polynomial problem.
-The authors state that the required CPU time depends strongly on the structure of the input data, so no closed formula to estimate the system size dependence can be given.
-A complete CPM analysis for a co-authorship network with $127.000$ links takes less than 2 hours on a PC\footnote{No details about the PC are given in the paper.}.
-I assume time complexity will not be a problem because my dataset contains $18.404$ edges in total, when not applying any threshold.
+Determining all cliques within a graph gives rise to a non-polynomial problem.
+The authors state that the required CPU time largely depends on the structure of the input data, so no closed formula can be given to estimate the system size dependence.
+A complete CPM analysis of a co-authorship network with $127.000$ links takes less than two hours on a PC\footnote{The paper provides no details about the PC.}.
+I assume that time complexity will not be a problem as my dataset contains $18.404$ edges in total when no threshold is being applied.
 
 \section{Future Work}
-As this paper discusses only one popular method, an extensive literature research should follow, finding out more methods solving the problem.
-Also, a closer look at more recent work would be necessary.
-It would be also interesting to find a good model for calculating edge weights with respect to scientific collaboration definitions.
-The visualization of the community evolution remains open and would be a broad topic, but exciting to investigate further.
+As this paper discusses only one popular method, an extensive literature research should follow, to check out more methods for solving the problem.
+In addition, a closer look at more recent work would be necessary.
+It would be equally interesting to come up with a good model for calculating edge weights with respect to the definition of scientific collaboration.
+The visualization of the community evolution, which remains open, would be a broad and exciting topic to investigate further.
 
